---
title: "01. Demographics"
author: "Nicolas L. Camacho"
date: "`r Sys.Date()`"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set working directory
knitr::opts_knit$set(root.dir = "C:/Users/nlc22/Documents/NicolasCamacho/fmri_reward/analysis_data")
```

# Load packages
```{r, message = FALSE}
library(tidyverse)
library(car)
library(emmeans)
```

# Load dataset, retain only demographics data, then separate into baseline & follow-up samples
```{r, message = FALSE}
all_data <- read_csv("final_share_dataset.csv") %>% 
  dplyr::select(., subj:ocd_past_base, pfc_s_mean_base) %>% 
  mutate_at(c("child_sex", "child_race", "child_hisp",
              "reporter_base", "reporter_fu"), as_factor)

base_data <- all_data %>% filter(., base_sample == 1)

fu_data <- base_data %>% filter(., fu_sample == 1)
```

# Summarize demographics for baseline sample
```{r}
base_summary <- base_data %>% 
  dplyr::summarize(
    cnt_male = sum(child_sex == "male"),
    perc_male = (sum(child_sex == "male")/length(child_sex))*100,
    
    cnt_fem = sum(child_sex == "female"),
    perc_fem = (sum(child_sex == "female")/length(child_sex))*100,
    
    min_age = min(child_age_base),
    max_age = max(child_age_base),
    mean_age = mean(child_age_base),
    sd_age = sd(child_age_base),
    
    cnt_white = sum(child_race == "white"),
    perc_white = (sum(child_race == "white")/length(child_race))*100,
    cnt_black = sum(child_race == "black"),
    perc_black = (sum(child_race == "black")/length(child_race))*100,
    cnt_asian = sum(child_race == "asian"),
    perc_asian = (sum(child_race == "asian")/length(child_race))*100,
    cnt_aian = sum(child_race == "aian"),
    perc_aian = (sum(child_race == "aian")/length(child_race))*100,
    cnt_white_black = sum(child_race == "white_black"),
    perc_white_black = (sum(child_race == "white_black")/length(child_race))*100,
    cnt_white_asian = sum(child_race == "white_asian"),
    perc_white_asian = (sum(child_race == "white_asian")/length(child_race))*100,
    cnt_white_nhopi = sum(child_race == "white_nhopi"),
    perc_white_nhopi = (sum(child_race == "white_nhopi")/length(child_race))*100,
    cnt_multi_unspec = sum(child_race == "mixed - unspec"),
    perc_multi_unspec = (sum(child_race == "mixed - unspec")/length(child_race))*100,
    cnt_unspec = sum(child_race == "unspec"),
    perc_unspec = (sum(child_race == "unspec")/length(child_race))*100,
    
    cnt_hisp = sum(child_hisp == "yes"),
    perc_hisp = (sum(child_hisp == "yes")/length(child_hisp))*100,
    
    cnt_mom_rep = sum(reporter_base == "bio_mom"),
    perc_mom_rep = (sum(reporter_base == "bio_mom")/length(reporter_base))*100,
    cnt_dad_rep = sum(reporter_base == "bio_dad"),
    perc_dad_rep = (sum(reporter_base == "bio_dad")/length(reporter_base))*100,
    
    min_income = min(na.omit(fam_income_base)),
    max_income = max(na.omit(fam_income_base)),
    mean_income = mean(na.omit(fam_income_base)),
    median_income = median(na.omit(fam_income_base)),
    sd_income = sd(na.omit(fam_income_base)),
    
    cnt_below25k = sum(na.omit(fam_income_base) < 25000),
    perc_below25k = (sum(na.omit(fam_income_base) < 25000)/length(fam_income_base))*100,
    cnt_25_49k = sum(na.omit(fam_income_base) > 24999 & na.omit(fam_income_base) < 50000),
    perc_25_49k = (sum(na.omit(fam_income_base) > 24999 & na.omit(fam_income_base) < 50000)/length(fam_income_base))*100,
    cnt_50_74k = sum(na.omit(fam_income_base) > 49999 & na.omit(fam_income_base) < 75000),
    perc_50_74k = (sum(na.omit(fam_income_base) > 49999 & na.omit(fam_income_base) < 75000)/length(fam_income_base))*100,
    cnt_75_99k = sum(na.omit(fam_income_base) > 74999 & na.omit(fam_income_base) < 100000),
    perc_75_99k = (sum(na.omit(fam_income_base) > 74999 & na.omit(fam_income_base) < 100000)/length(fam_income_base))*100,
    cnt_100k_plus = sum(na.omit(fam_income_base) > 100000),
    perc_100k_plus = (sum(na.omit(fam_income_base) > 100000)/length(fam_income_base))*100,
    
    min_i2n = min(na.omit(i2n_base)),
    max_i2n = max(na.omit(i2n_base)),
    mean_i2n = mean(na.omit(i2n_base)),
    median_i2n = median(na.omit(i2n_base)),
    sd_i2n = sd(na.omit(i2n_base)),
    
    cnt_at_below_pov = sum(na.omit(i2n_base) <= 1),
    perc_at_below_pov = (sum(na.omit(i2n_base) <= 1)/length(i2n_base))*100,
    cnt_above_pov = sum(na.omit(i2n_base) > 1),
    perc_above_pov = (sum(na.omit(i2n_base) > 1)/length(i2n_base))*100,
    
    cnt_mdd_current = sum(na.omit(mdd_current_base)),
    perc_mdd_current = (sum(na.omit(mdd_current_base))/length(mdd_current_base))*100,
    cnt_mdd_past = sum(na.omit(mdd_past_base)),
    perc_mdd_past = (sum(na.omit(mdd_past_base))/length(mdd_past_base))*100,
    cnt_adhd_current = sum(na.omit(adhd_current_base)),
    perc_adhd_current = (sum(na.omit(adhd_current_base))/length(adhd_current_base))*100,
    cnt_odd_current = sum(na.omit(odd_current_base)),
    perc_odd_current = (sum(na.omit(odd_current_base))/length(odd_current_base))*100,
    cnt_gad_current = sum(na.omit(gad_current_base)),
    perc_gad_current = (sum(na.omit(gad_current_base))/length(gad_current_base))*100,
    cnt_socanx_current = sum(na.omit(socanx_current_base)),
    perc_socanx_current = (sum(na.omit(socanx_current_base))/length(socanx_current_base))*100,
    cnt_ocd_past = sum(na.omit(ocd_past_base)),
    perc_ocd_past = (sum(na.omit(ocd_past_base))/length(ocd_past_base))*100,
    cnt_spec_phobia_past = sum(na.omit(spec_phobia_past_base)),
    perc_spec_phobia_past = (sum(na.omit(spec_phobia_past_base))/length(spec_phobia_past_base))*100
  )
base_summary
```

# Summarize demographics for follow-up sample
```{r}
fu_summary <- fu_data %>% 
  dplyr::summarize(
    cnt_male = sum(child_sex == "male"),
    perc_male = (sum(child_sex == "male")/length(child_sex))*100,
    
    cnt_fem = sum(child_sex == "female"),
    perc_fem = (sum(child_sex == "female")/length(child_sex))*100,
    
    min_age = min(child_age_fu),
    max_age = max(child_age_fu),
    mean_age = mean(child_age_fu),
    sd_age = sd(child_age_fu),
    
    cnt_white = sum(child_race == "white"),
    perc_white = (sum(child_race == "white")/length(child_race))*100,
    cnt_black = sum(child_race == "black"),
    perc_black = (sum(child_race == "black")/length(child_race))*100,
    cnt_asian = sum(child_race == "asian"),
    perc_asian = (sum(child_race == "asian")/length(child_race))*100,
    cnt_aian = sum(child_race == "aian"),
    perc_aian = (sum(child_race == "aian")/length(child_race))*100,
    cnt_white_black = sum(child_race == "white_black"),
    perc_white_black = (sum(child_race == "white_black")/length(child_race))*100,
    cnt_white_asian = sum(child_race == "white_asian"),
    perc_white_asian = (sum(child_race == "white_asian")/length(child_race))*100,
    cnt_white_nhopi = sum(child_race == "white_nhopi"),
    perc_white_nhopi = (sum(child_race == "white_nhopi")/length(child_race))*100,
    cnt_multi_unspec = sum(child_race == "mixed - unspec"),
    perc_multi_unspec = (sum(child_race == "mixed - unspec")/length(child_race))*100,
    cnt_unspec = sum(child_race == "unspec"),
    perc_unspec = (sum(child_race == "unspec")/length(child_race))*100,
    
    cnt_hisp = sum(child_hisp == "yes"),
    perc_hisp = (sum(child_hisp == "yes")/length(child_hisp))*100,
    
    cnt_mom_rep = sum(reporter_fu == "bio_mom"),
    perc_mom_rep = (sum(reporter_fu == "bio_mom")/length(reporter_fu))*100,
    cnt_dad_rep = sum(reporter_fu == "bio_dad"),
    perc_dad_rep = (sum(reporter_fu == "bio_dad")/length(reporter_fu))*100,
    
    min_income = min(na.omit(fam_income_fu)),
    max_income = max(na.omit(fam_income_fu)),
    mean_income = mean(na.omit(fam_income_fu)),
    median_income = median(na.omit(fam_income_fu)),
    sd_income = sd(na.omit(fam_income_fu)),
    
    cnt_below25k = sum(na.omit(fam_income_fu) < 25000),
    perc_below25k = (sum(na.omit(fam_income_fu) < 25000)/length(fam_income_fu))*100,
    cnt_25_49k = sum(na.omit(fam_income_fu) > 24999 & na.omit(fam_income_fu) < 50000),
    perc_25_49k = (sum(na.omit(fam_income_fu) > 24999 & na.omit(fam_income_fu) < 50000)/length(fam_income_fu))*100,
    cnt_50_74k = sum(na.omit(fam_income_fu) > 49999 & na.omit(fam_income_fu) < 75000),
    perc_50_74k = (sum(na.omit(fam_income_fu) > 49999 & na.omit(fam_income_fu) < 75000)/length(fam_income_fu))*100,
    cnt_75_99k = sum(na.omit(fam_income_fu) > 74999 & na.omit(fam_income_fu) < 100000),
    perc_75_99k = (sum(na.omit(fam_income_fu) > 74999 & na.omit(fam_income_fu) < 100000)/length(fam_income_fu))*100,
    cnt_100k_plus = sum(na.omit(fam_income_fu) > 100000),
    perc_100k_plus = (sum(na.omit(fam_income_fu) > 100000)/length(fam_income_fu))*100,
    
    min_i2n = min(na.omit(i2n_fu)),
    max_i2n = max(na.omit(i2n_fu)),
    mean_i2n = mean(na.omit(i2n_fu)),
    median_i2n = median(na.omit(i2n_fu)),
    sd_i2n = sd(na.omit(i2n_fu)),
    
    cnt_at_below_pov = sum(na.omit(i2n_fu) <= 1),
    perc_at_below_pov = (sum(na.omit(i2n_fu) <= 1)/length(i2n_fu))*100,
    cnt_above_pov = sum(na.omit(i2n_fu) > 1),
    perc_above_pov = (sum(na.omit(i2n_fu) > 1)/length(i2n_fu))*100,
    
    cnt_mdd_current = sum(na.omit(mdd_current_base)),
    perc_mdd_current = (sum(na.omit(mdd_current_base))/length(mdd_current_base))*100,
    cnt_mdd_past = sum(na.omit(mdd_past_base)),
    perc_mdd_past = (sum(na.omit(mdd_past_base))/length(mdd_past_base))*100,
    cnt_adhd_current = sum(na.omit(adhd_current_base)),
    perc_adhd_current = (sum(na.omit(adhd_current_base))/length(adhd_current_base))*100,
    cnt_odd_current = sum(na.omit(odd_current_base)),
    perc_odd_current = (sum(na.omit(odd_current_base))/length(odd_current_base))*100,
    cnt_gad_current = sum(na.omit(gad_current_base)),
    perc_gad_current = (sum(na.omit(gad_current_base))/length(gad_current_base))*100,
    cnt_socanx_current = sum(na.omit(socanx_current_base)),
    perc_socanx_current = (sum(na.omit(socanx_current_base))/length(socanx_current_base))*100,
    cnt_ocd_past = sum(na.omit(ocd_past_base)),
    perc_ocd_past = (sum(na.omit(ocd_past_base))/length(ocd_past_base))*100,
    cnt_spec_phobia_past = sum(na.omit(spec_phobia_past_base)),
    perc_spec_phobia_past = (sum(na.omit(spec_phobia_past_base))/length(spec_phobia_past_base))*100
  )
fu_summary
```

# Assess the extent to which the baseline sample differs demographically from omitted participants

## Create a column to clearly differentiate between the baseline and omitted samples
```{r}
all_data_BvO <- all_data %>% 
  mutate(base_v_omit = factor(case_when(base_sample == 1 ~ "baseline",
                                        base_sample == 0 ~ "omitted")))
# check dummy contrast code
contrasts(all_data_BvO$base_v_omit)
```

### Child Age (at baseline)
```{r}
baseAge_full_bvo <- lm(child_age_base ~ 1 + base_v_omit, data = all_data_BvO)
Anova(baseAge_full_bvo, type = "III")
emmeans(baseAge_full_bvo, "base_v_omit")
pairs(emmeans(baseAge_full_bvo, "base_v_omit"))
```

### Child Sex assigned at birth
```{r}
sex_bvo_propTest <- all_data_BvO %>%
  group_by(base_v_omit) %>% 
  summarise(male = sum(child_sex == "male"),
            female = sum(child_sex == "female"))

prop.test(x = as.matrix(sex_bvo_propTest[-1]), alternative = 'two.sided')
```

### Child Race

#### First, given small sample sizes for each multi-racial category, collapse across them
#### Also, omit participants without specified race
```{r, warning = F}
race_data_BvO <- all_data_BvO %>% 
  dplyr::select(subj, child_race, contains("_v_")) %>% 
  mutate(child_race = factor(case_when(child_race == "white" ~ "white",
                                       child_race == "black" ~ "black",
                                       child_race == "asian" ~ "asian",
                                       child_race == "aian" ~ "aian",
                                       child_race == "white_asian" |
                                         child_race == "white_nhopi" |
                                         child_race == "white_black" |
                                         child_race == "mixed - unspec" ~ "multi")))

race_bvo_summary <- race_data_BvO %>%
  group_by(base_v_omit) %>% 
  summarise(white = sum(na.omit(child_race) == "white"),
            black = sum(na.omit(child_race) == "black"),
            asian = sum(na.omit(child_race) == "asian"),
            aian = sum(na.omit(child_race) == "aian"),
            multi = sum(na.omit(child_race) == "multi"))
chisq.test(as.matrix(race_bvo_summary[-1]))
```

### Child Ethnicity
```{r}
ethnic_bvo_summary <- all_data_BvO %>%
  group_by(base_v_omit) %>% 
  summarise(hisp = sum(na.omit(child_hisp == "yes")),
            non_hisp = sum(na.omit(child_hisp) == "no")) 
prop.test(x = as.matrix(ethnic_bvo_summary[-1]), alternative = 'two.sided')
```

### Income-to-Needs
```{r}
basei2n_full_bvo <- lm(i2n_base ~ 1 + base_v_omit, data = all_data_BvO)
Anova(basei2n_full_bvo, type = "III")
emmeans(basei2n_full_bvo, "base_v_omit")
pairs(emmeans(basei2n_full_bvo, "base_v_omit"))
```

### PFC-S scores (at baseline)
```{r}
base_pfcs_full_bvo <- lm(pfc_s_mean_base ~ 1 + base_v_omit, data = all_data_BvO)
Anova(base_pfcs_full_bvo, type = "III")
emmeans(base_pfcs_full_bvo, "base_v_omit")
pairs(emmeans(base_pfcs_full_bvo, "base_v_omit"))
```

# Assess the extent to which the follow-up sample differs demographically from participants with baseline data that were omitted

## Create a column to clearly differentiate between the follow-up and omitted baseline samples
```{r}
all_data_FvBO <- all_data %>% 
  filter(base_sample == 1) %>% 
  mutate(fu_v_baseOmit = factor(case_when(fu_sample == 1 ~ "fu",
                                          fu_sample == 0 ~ "baseOmitted")))
# check dummy contrast code
contrasts(all_data_FvBO$fu_v_baseOmit)
```

### Child Age (at baseline)
```{r}
baseAge_full_fvbo <- lm(child_age_base ~ 1 + fu_v_baseOmit, data = all_data_FvBO)
Anova(baseAge_full_fvbo, type = "III")
emmeans(baseAge_full_fvbo, "fu_v_baseOmit")
pairs(emmeans(baseAge_full_fvbo, "fu_v_baseOmit"))
```

### Child Sex assigned at birth
```{r}
sex_fvbo_propTest <- all_data_FvBO %>%
  group_by(fu_v_baseOmit) %>% 
  summarise(male = sum(child_sex == "male"),
            female = sum(child_sex == "female"))

prop.test(x = as.matrix(sex_fvbo_propTest[-1]), alternative = 'two.sided')
```

### Child Race

#### First, given small sample sizes for each multi-racial category, collapse across them
#### Also, omit participants without specified race
```{r, warning = F}
race_data_FvBO <- all_data_FvBO %>% 
  dplyr::select(subj, child_race, contains("_v_")) %>% 
  mutate(child_race = factor(case_when(child_race == "white" ~ "white",
                                       child_race == "black" ~ "black",
                                       child_race == "asian" ~ "asian",
                                       child_race == "aian" ~ "aian",
                                       child_race == "white_asian" |
                                         child_race == "white_nhopi" |
                                         child_race == "white_black" |
                                         child_race == "mixed - unspec" ~ "multi")))

race_fvbo_summary <- race_data_FvBO %>%
  group_by(fu_v_baseOmit) %>% 
  summarise(white = sum(na.omit(child_race) == "white"),
            black = sum(na.omit(child_race) == "black"),
            asian = sum(na.omit(child_race) == "asian"),
            aian = sum(na.omit(child_race) == "aian"),
            multi = sum(na.omit(child_race) == "multi"))
chisq.test(as.matrix(race_fvbo_summary[-1]))
```

### Child Ethnicity
```{r, warning = F}
ethnic_fvbo_summary <- all_data_FvBO %>%
  group_by(fu_v_baseOmit) %>% 
  summarise(hisp = sum(na.omit(child_hisp == "yes")),
            non_hisp = sum(na.omit(child_hisp) == "no")) 
prop.test(x = as.matrix(ethnic_fvbo_summary[-1]), alternative = 'two.sided')
```

### Income-to-Needs
```{r}
basei2n_full_fvbo <- lm(i2n_base ~ 1 + fu_v_baseOmit, data = all_data_FvBO)
Anova(basei2n_full_fvbo, type = "III")
emmeans(basei2n_full_fvbo, "fu_v_baseOmit")
pairs(emmeans(basei2n_full_fvbo, "fu_v_baseOmit"))
```

### PFC-S scores (at baseline)
```{r}
base_pfcs_full_fvbo <- lm(pfc_s_mean_base ~ 1 + fu_v_baseOmit, data = all_data_FvBO)
Anova(base_pfcs_full_fvbo, type = "III")
emmeans(base_pfcs_full_fvbo, "fu_v_baseOmit")
pairs(emmeans(base_pfcs_full_fvbo, "fu_v_baseOmit"))
```

