---
title: "03. Outlier Detection"
author: "Nicolas L. Camacho"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set working directory
knitr::opts_knit$set(root.dir = "C:/Users/nlc22/Documents/NicolasCamacho/fmri_reward/analysis_data")
```

# Load package
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
```

# Load dataset, retain variables of interest (standardized), and split into baseline and follow-up samples
```{r, message = FALSE}
all_data <- read_csv("final_share_dataset.csv")

base_data <- all_data %>% 
  filter(base_sample == 1) %>% 
  dplyr::select(., subj, z_child_age_base, z_pfc_s_mean_base, z_bdi_mean_base, 
                contains("avg") & contains("z_"), contains("RvN") & contains("z_"))

fu_data <- all_data %>% 
  filter(fu_sample == 1) %>% 
  dplyr::select(., subj, z_child_age_fu, z_pfc_s_mean_fu, z_bdi_mean_fu,
                contains("avg") & contains("z_"), 
                contains("RvN") & contains("z_"))
```

# Identify participants that are outliers for each model according to the DFBETA value related to the regression coefficient between the fMRI reward/salience reactivity value and PFC-S scores

## Baseline analyses

### Left Amygdala
```{r}
# Run the model
rln_lamyg_base <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                  z_avgRLvN_HO_LAmyg, data = base_data)
# Identify & save column identifying DFBETA outliers
base_dfbo <- base_data %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rln_lamyg_base))) %>% 
  rename(., dfb_rln_lamyg_base = z_avgRLvN_HO_LAmyg) %>%
  dplyr::select(., subj, dfb_rln_lamyg_base) %>% 
  mutate(dfbo_rln_lamyg_base = if_else(abs(dfb_rln_lamyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rln_lamyg_base) %>% 
  left_join(base_data, ., by = "subj")
```

### Right Amygdala
```{r}
# Run the model
rln_ramyg_base <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                  z_avgRLvN_HO_RAmyg, data = base_data)
# Identify & save column identifying DFBETA outliers
base_dfbo <- base_dfbo %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rln_ramyg_base))) %>% 
  rename(., dfb_rln_ramyg_base = z_avgRLvN_HO_RAmyg) %>%
  dplyr::select(., subj, dfb_rln_ramyg_base) %>% 
  mutate(dfbo_rln_ramyg_base = if_else(abs(dfb_rln_ramyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rln_ramyg_base) %>% 
  left_join(base_dfbo, ., by = "subj")
```

### Left Caudate
```{r}
# Run the model
rn_lcaud_base <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                  z_RvN_2018_LCaud, data = base_data)
# Identify & save column identifying DFBETA outliers
base_dfbo <- base_dfbo %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rn_lcaud_base))) %>% 
  rename(., dfb_rn_lcaud_base = z_RvN_2018_LCaud) %>%
  dplyr::select(., subj, dfb_rn_lcaud_base) %>% 
  mutate(dfbo_rn_lcaud_base = if_else(abs(dfb_rn_lcaud_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rn_lcaud_base) %>% 
  left_join(base_dfbo, ., by = "subj")
```

### Right Caudate
```{r}
# Run the model
rn_rcaud_base <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                  z_RvN_2018_RCaud, data = base_data)
# Identify & save column identifying DFBETA outliers
base_dfbo <- base_dfbo %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rn_rcaud_base))) %>% 
  rename(., dfb_rn_rcaud_base = z_RvN_2018_RCaud) %>%
  dplyr::select(., subj, dfb_rn_rcaud_base) %>% 
  mutate(dfbo_rn_rcaud_base = if_else(abs(dfb_rn_rcaud_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rn_rcaud_base) %>% 
  left_join(base_dfbo, ., by = "subj")
```

### Right pACC
```{r}
# Run the model
rn_RmPFC_base <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                  z_RvN_2021_RmPFC, data = base_data)
# Identify & save column identifying DFBETA outliers
base_dfbo <- base_dfbo %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rn_RmPFC_base))) %>% 
  rename(., dfb_rn_RmPFC_base = z_RvN_2021_RmPFC) %>%
  dplyr::select(., subj, dfb_rn_RmPFC_base) %>% 
  mutate(dfbo_rn_RmPFC_base = if_else(abs(dfb_rn_RmPFC_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rn_RmPFC_base) %>% 
  left_join(base_dfbo, ., by = "subj")
```

## Follow-Up

### Left Amygdala
```{r}
# Run the model
rln_lamyg_fu <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu + 
                     z_avgRLvN_HO_LAmyg, data = fu_data)
# Identify & save column identifying DFBETA outliers
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rln_lamyg_fu))) %>% 
  rename(., dfb_rln_lamyg_fu = z_avgRLvN_HO_LAmyg) %>%
  dplyr::select(., subj, dfb_rln_lamyg_fu) %>% 
  mutate(dfbo_rln_lamyg_fu = if_else(abs(dfb_rln_lamyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rln_lamyg_fu) %>% 
  left_join(fu_data, ., by = "subj")
```

### Right Amygdala
```{r}
# Run the model
rln_ramyg_fu <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu + 
                    z_avgRLvN_HO_RAmyg, data = fu_data)
# Identify & save column identifying DFBETA outliers
fu_dfbo <- fu_dfbo %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rln_ramyg_fu))) %>% 
  rename(., dfb_rln_ramyg_fu = z_avgRLvN_HO_RAmyg) %>%
  dplyr::select(., subj, dfb_rln_ramyg_fu) %>% 
  mutate(dfbo_rln_ramyg_fu = if_else(abs(dfb_rln_ramyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rln_ramyg_fu) %>% 
  left_join(fu_dfbo, ., by = "subj")
```

### Left Caudate
```{r}
# Run the model
rn_lcaud_fu <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu + 
                    z_RvN_2018_LCaud, data = fu_data)
# Identify & save column identifying DFBETA outliers
fu_dfbo <- fu_dfbo %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rn_lcaud_fu))) %>% 
  rename(., dfb_rn_lcaud_fu = z_RvN_2018_LCaud) %>%
  dplyr::select(., subj, dfb_rn_lcaud_fu) %>% 
  mutate(dfbo_rn_lcaud_fu = if_else(abs(dfb_rn_lcaud_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rn_lcaud_fu) %>% 
  left_join(fu_dfbo, ., by = "subj")
```

### Right Caudate
```{r}
# Run the model
rn_rcaud_fu <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu + 
                    z_RvN_2018_RCaud, data = fu_data)
# Identify & save column identifying DFBETA outliers
fu_dfbo <- fu_dfbo %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rn_rcaud_fu))) %>% 
  rename(., dfb_rn_rcaud_fu = z_RvN_2018_RCaud) %>%
  dplyr::select(., subj, dfb_rn_rcaud_fu) %>% 
  mutate(dfbo_rn_rcaud_fu = if_else(abs(dfb_rn_rcaud_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rn_rcaud_fu) %>% 
  left_join(fu_dfbo, ., by = "subj")
```

### Right mPFC
```{r}
# Run the model
rn_RmPFC_fu <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu + 
                   z_RvN_2021_RmPFC, data = fu_data)
# Identify & save column identifying DFBETA outliers
fu_dfbo <- fu_dfbo %>% dplyr::select(., subj) %>%
  bind_cols(., data.frame(dfbetas(rn_RmPFC_fu))) %>% 
  rename(., dfb_rn_RmPFC_fu = z_RvN_2021_RmPFC) %>%
  dplyr::select(., subj, dfb_rn_RmPFC_fu) %>% 
  mutate(dfbo_rn_RmPFC_fu = if_else(abs(dfb_rn_RmPFC_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -dfb_rn_RmPFC_fu) %>% 
  left_join(fu_dfbo, ., by = "subj")
```

# Count of outliers identified per model

## Baseline
```{r}
base_dfbo %>% 
  summarise(n_rln_lamyg = sum(.$dfbo_rln_lamyg_base),
            n_rln_ramyg = sum(.$dfbo_rln_ramyg_base),
            n_rn_lcaud = sum(.$dfbo_rn_lcaud_base),
            n_rn_rcaud = sum(.$dfbo_rn_rcaud_base),
            n_rn_RmPFC = sum(.$dfbo_rn_RmPFC_base))
```

## Follow-up
```{r}
fu_dfbo %>% 
  summarise(n_rln_lamyg = sum(.$dfbo_rln_lamyg_fu),
            n_rln_ramyg = sum(.$dfbo_rln_ramyg_fu),
            n_rn_lcaud = sum(.$dfbo_rn_lcaud_fu),
            n_rn_rcaud = sum(.$dfbo_rn_rcaud_fu),
            n_rn_RmPFC = sum(.$dfbo_rn_RmPFC_fu))
```

# Save dataframe for regression analyses
```{r}
all_data <- base_dfbo %>% dplyr::select(., subj, dfbo_rln_ramyg_base) %>% 
  left_join(all_data, ., by = "subj") %>% 
  relocate(dfbo_rln_ramyg_base, .after = dfbo_rln_lamyg_base)

all_data <- fu_dfbo %>% dplyr::select(., subj, dfbo_rln_ramyg_fu) %>% 
  left_join(all_data, ., by = "subj") %>% 
  relocate(dfbo_rln_ramyg_fu, .after = dfbo_rln_lamyg_fu)

write.csv(all_data, file = "final_share_dataset.csv", row.names = FALSE)
```
