---
title: "S1. Analysis of Behavioral Doors Guessing Task Data"
author: "Nicolas L. Camacho"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set working directory
knitr::opts_knit$set(root.dir = "C:/Users/nlc22/Documents/NicolasCamacho/fmri_reward/analysis_data")
```

# Load packages
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(nnet)
library(lme4)
library(sjPlot)
```

# Load datasets
```{r, message = FALSE}
doors_base <- read_csv("final_doors_behav_base.csv")
doors_fu <- read_csv("final_doors_behav_fu.csv")
```

# Make the Trial Type and Response variables factors
## Code Trial Type using unweighted effects coding

### Baseline
```{r}
doors_base <- doors_base %>% 
  filter(!is.na(trial_type)) %>%
  mutate(trial_type = factor(trial_type, labels = c("Loss", "Neutral", "Reward")),
         response = factor(response, labels = c("0", "1", "non")))

# check current coding scheme
contrasts(doors_base$trial_type)
# update to unweighted effects coding
contrasts(doors_base$trial_type) <- contr.sum
# check new coding scheme
contrasts(doors_base$trial_type)
```

### Follow-Up
```{r}
doors_fu <- doors_fu %>% 
  filter(!is.na(trial_type)) %>%
  mutate(trial_type = factor(trial_type, labels = c("Loss", "Neutral", "Reward")),
         response = factor(response, labels = c("0", "1", "non")))

# check current coding scheme
contrasts(doors_fu$trial_type)
# update to unweighted effects coding
contrasts(doors_fu$trial_type) <- contr.sum
# check new coding scheme
contrasts(doors_fu$trial_type)
```

# Analyze whether Response behavior differed between Trial Types

## Note: Because runs are nested within participants, this nested structure is specified in a multilevel model. Since, Response is a binary categorical variable, a generalized linear multilevel model with binary logistic regression specifications is used.

### Baseline
```{r}
null_resp_lm_base <- multinom(response ~ 1, random = 1|subj/run, data = doors_base)
resp_lm_base <- multinom(response ~ 1 + trial_type, random = 1|subj/run, data = doors_base)
anova(null_resp_lm_base, resp_lm_base)
```

### Follow-Up
```{r}
null_resp_lm_fu <- multinom(response ~ 1, random = 1|subj/run, data = doors_fu)
resp_lm_fu <- multinom(response ~ 1 + trial_type, random = 1|subj/run, data = doors_fu)
anova(null_resp_lm_fu, resp_lm_fu)
```

# Analyze whether Response Times differed based on Trial Types and Response Options

## Note: Because runs are nested within participants, this nested structure is specified in a multilevel model.

### Baseline
```{r}
# Remove non-responses because RT will be maxed out for those
doors_base_rt <- doors_base %>% 
  filter(response != "non") %>% mutate(response = factor(response, labels = c("0", "1")))
# Make the response variable unweighted effects coded (trial_type already is)
contrasts(doors_base_rt$response) <- contr.sum
contrasts(doors_base_rt$response)
# Null model
null_rt_lm_base <- lmer(resp_time ~ 1 + (1|subj/run), REML = F, data = doors_base_rt)
# Model with trial_type
rt_tt_lm_base <- lmer(resp_time ~ 1 + trial_type + (1|subj/run), REML = F, data = doors_base_rt)
anova(null_rt_lm_base, rt_tt_lm_base)
# Model with response
rt_resp_lm_base <- lmer(resp_time ~ 1 + response + (1|subj/run), REML = F, data = doors_base_rt)
anova(null_rt_lm_base, rt_resp_lm_base)
# Model with trial_type by response interaction
rt_tt_resp_lm_base <- lmer(resp_time ~ 1 + trial_type*response + (1|subj/run), REML = F, data = doors_base_rt)
anova(null_rt_lm_base, rt_tt_resp_lm_base)
```

### Follow-Up
```{r}
# Remove non-responses because RT will be maxed out for those
doors_fu_rt <- doors_fu %>% 
  filter(response != "non") %>% mutate(response = factor(response, labels = c("0", "1")))
# Make the response variable unweighted effects coded (trial_type already is)
contrasts(doors_fu_rt$response) <- contr.sum
contrasts(doors_fu_rt$response)
# Null model
null_rt_lm_fu <- lmer(resp_time ~ 1 + (1|subj/run), REML = F, data = doors_fu_rt)
# Model with trial_type
rt_tt_lm_fu <- lmer(resp_time ~ 1 + trial_type + (1|subj/run), REML = F, data = doors_fu_rt)
anova(null_rt_lm_fu, rt_tt_lm_fu)
# Model with response
rt_resp_lm_fu <- lmer(resp_time ~ 1 + response + (1|subj/run), REML = F, data = doors_fu_rt)
anova(null_rt_lm_fu, rt_resp_lm_fu)
# Model with trial_type by response interaction
rt_tt_resp_lm_fu <- lmer(resp_time ~ 1 + trial_type*response + (1|subj/run), REML = F, data = doors_fu_rt)
anova(null_rt_lm_fu, rt_tt_resp_lm_fu)
```





