---
title: "S4. Prospective Regression Sensitivity Analyses -- Outliers Included"
author: "Nicolas L. Camacho"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set working directory
knitr::opts_knit$set(root.dir = "C:/Users/nlc22/Documents/NicolasCamacho/fmri_reward/analysis_data")
```

# Load packages
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(broom)
library(sensemakr)
library(lm.beta)
library(lmtest)
library(miceadds)
```

# Load dataset
```{r, message = FALSE}
fu_data <- read_csv("final_share_dataset.csv") %>% 
  filter(fu_sample == 1) %>%
  dplyr::select(., subj, fam_code, z_child_age_fu, z_pfc_s_mean_fu, z_bdi_mean_fu, 
                contains("avg") & contains("z_"), contains("RvN") & contains("z_"),
                contains("dfbo") & contains("fu"))
```

# Run regression analyses (covariates: child age at FU, parent BDI-II at FU)

## Restricted model used across all other models.
```{r}
# run restricted model
restrict_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu,
                          cluster = "fam_code", data = fu_data)
summary(restrict_lm)
```

## Left Amygdala
```{r}
# run full model
rln_lamyg_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_avgRLvN_HO_LAmyg, cluster = "fam_code", data = fu_data)
# run full model without cluster robust SE's to retrieve adjusted R^2
rln_lamyg_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_avgRLvN_HO_LAmyg, data = fu_data)
# view results
summary(rln_lamyg_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(rln_lamyg_lm, level = 0.90) # consider only upper limit for 95% confidence that estimate is < 0
.12689 - .12671 # R^2 change
glance(rln_lamyg_lm_noClust)$adj.r.squared # adjusted R^2
```

## Right Amygdala
```{r}
# run full model
rln_ramyg_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_avgRLvN_HO_RAmyg, cluster = "fam_code", data = fu_data)
# run full model without cluster robust SE's to retrieve adjusted R^2
rln_ramyg_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_avgRLvN_HO_RAmyg, data = fu_data)
# view results
summary(rln_ramyg_lm)
confint(rln_ramyg_lm)
.13904 - .12671 # R^2 change
glance(rln_ramyg_lm_noClust)$adj.r.squared # adjusted R^2
```

## Left Caudate
```{r}
# run full model
rn_lcaud_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                    z_RvN_2018_LCaud, cluster = "fam_code", data = fu_data)
# run full model without cluster robust SE's to retrieve adjusted R^2
rn_lcaud_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                    z_RvN_2018_LCaud, data = fu_data)
# view results
summary(rn_lcaud_lm)
confint(rn_lcaud_lm, level = 0.95) # 95% CI
0.13296 - .12671 # R^2 change
glance(rn_lcaud_lm_noClust)$adj.r.squared # adjusted R^2
```

## Right Caudate
```{r}
# run full model
rn_rcaud_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                    z_RvN_2018_RCaud, cluster = "fam_code", data = fu_data)
# run full model without cluster robust SE's to retrieve adjusted R^2
rn_rcaud_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                    z_RvN_2018_RCaud, data = fu_data)
# view results
summary(rn_rcaud_lm)
confint(rn_rcaud_lm, level = 0.95) # 95% CI
.12813 - .12671 # R^2 change
glance(rn_rcaud_lm_noClust)$adj.r.squared # adjusted R^2
```

## Right mPFC
```{r}
# run full model
rn_RmPFC_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                   z_RvN_2021_RmPFC, cluster = "fam_code", data = fu_data)
# run full model without cluster robust SE's to retrieve adjusted R^2
rn_RmPFC_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                   z_RvN_2021_RmPFC, data = fu_data)
# view results
summary(rn_RmPFC_lm)
confint(rn_RmPFC_lm, level = 0.95) # 95% CI
.13726 - .12671 # R^2 change
glance(rn_RmPFC_lm_noClust)$adj.r.squared # adjusted R^2
```

# Create plots

## These plots include the outliers that were removed in the main analyses. Outliers are depicted in red.

## Left Amygdala
```{r, message = F}
rln_lamyg_pfcs <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rln_lamyg_brn <- lm(z_avgRLvN_HO_LAmyg ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rln_lamyg_resid <- data.frame(rln_lamyg_pfcs$residuals, rln_lamyg_brn$residuals,
                              fu_data$dfbo_rln_lamyg_fu) %>% 
  rename(pfcs_resid = rln_lamyg_pfcs.residuals, brn_resid = rln_lamyg_brn.residuals,
         dfbo_rln_lamyg = fu_data.dfbo_rln_lamyg_fu) %>% 
  mutate(dfbo_rln_lamyg_col = case_when(dfbo_rln_lamyg == 0 ~ "black",
                                        dfbo_rln_lamyg == 1 ~ "red"))
plot_rln_lamyg_lm <- rln_lamyg_resid %>% 
  ggplot(aes(x = brn_resid, y = pfcs_resid)) +
  geom_point(color = factor(rln_lamyg_resid$dfbo_rln_lamyg_col)) +
  geom_smooth(method = "lm") + 
  xlab("Baseline RLvN (z-score residuals)") + ylab("Follow-Up PFC-S Scores (z-score residuals)") + 
  theme_classic() +
  theme(legend.position = "none")
plot_rln_lamyg_lm
```

## Right Amygdala
```{r, message = F}
rln_ramyg_pfcs <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rln_ramyg_brn <- lm(z_avgRLvN_HO_RAmyg ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rln_ramyg_resid <- data.frame(rln_ramyg_pfcs$residuals, rln_ramyg_brn$residuals,
                              fu_data$dfbo_rln_ramyg_fu) %>% 
  rename(pfcs_resid = rln_ramyg_pfcs.residuals, brn_resid = rln_ramyg_brn.residuals,
         dfbo_rln_ramyg = fu_data.dfbo_rln_ramyg_fu) %>% 
  mutate(dfbo_rln_ramyg_col = case_when(dfbo_rln_ramyg == 0 ~ "black",
                                        dfbo_rln_ramyg == 1 ~ "red"))
plot_rln_ramyg_lm <- rln_ramyg_resid %>% 
  ggplot(aes(x = brn_resid, y = pfcs_resid)) +
  geom_point(color = factor(rln_ramyg_resid$dfbo_rln_ramyg_col)) +
  geom_smooth(method = "lm") + 
  xlab("Baseline RLvN (z-score residuals)") + ylab("Follow-Up PFC-S Scores (z-score residuals)") + 
  theme_classic() +
  theme(legend.position = "none")
plot_rln_ramyg_lm
```

## Left Caudate
```{r, message = F}
rn_lcaud_pfcs <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rn_lcaud_brn <- lm(z_RvN_2018_LCaud ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rn_lcaud_resid <- data.frame(rn_lcaud_pfcs$residuals, rn_lcaud_brn$residuals,
                              fu_data$dfbo_rn_lcaud_fu) %>% 
  rename(pfcs_resid = rn_lcaud_pfcs.residuals, brn_resid = rn_lcaud_brn.residuals,
         dfbo_rn_lcaud = fu_data.dfbo_rn_lcaud_fu) %>% 
  mutate(dfbo_rn_lcaud_col = case_when(dfbo_rn_lcaud == 0 ~ "black",
                                        dfbo_rn_lcaud == 1 ~ "red"))
plot_rn_lcaud_lm <- rn_lcaud_resid %>% 
  ggplot(aes(x = brn_resid, y = pfcs_resid)) +
  geom_point(color = factor(rn_lcaud_resid$dfbo_rn_lcaud_col)) +
  geom_smooth(method = "lm") + 
  xlab("Baseline RvN (z-score residuals)") + ylab("Follow-Up PFC-S Scores (z-score residuals)") + 
  theme_classic() +
  theme(legend.position = "none")
plot_rn_lcaud_lm
```


## Right Caudate
```{r, message = F}
rn_rcaud_pfcs <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rn_rcaud_brn <- lm(z_RvN_2018_RCaud ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rn_rcaud_resid <- data.frame(rn_rcaud_pfcs$residuals, rn_rcaud_brn$residuals,
                              fu_data$dfbo_rn_rcaud_fu) %>% 
  rename(pfcs_resid = rn_rcaud_pfcs.residuals, brn_resid = rn_rcaud_brn.residuals,
         dfbo_rn_rcaud = fu_data.dfbo_rn_rcaud_fu) %>% 
  mutate(dfbo_rn_rcaud_col = case_when(dfbo_rn_rcaud == 0 ~ "black",
                                        dfbo_rn_rcaud == 1 ~ "red"))
plot_rn_rcaud_lm <- rn_rcaud_resid %>% 
  ggplot(aes(x = brn_resid, y = pfcs_resid)) +
  geom_point(color = factor(rn_rcaud_resid$dfbo_rn_rcaud_col)) +
  geom_smooth(method = "lm") + 
  xlab("Baseline RvN (z-score residuals)") + ylab("Follow-Up PFC-S Scores (z-score residuals)") + 
  theme_classic() +
  theme(legend.position = "none")
plot_rn_rcaud_lm
```

## Right mPFC
```{r, message = F}
rn_RmPFC_pfcs <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rn_RmPFC_brn <- lm(z_RvN_2021_RmPFC ~ 1 + z_child_age_fu + z_bdi_mean_fu, data = fu_data)
rn_RmPFC_resid <- data.frame(rn_RmPFC_pfcs$residuals, rn_RmPFC_brn$residuals,
                              fu_data$dfbo_rn_RmPFC_fu) %>% 
  rename(pfcs_resid = rn_RmPFC_pfcs.residuals, brn_resid = rn_RmPFC_brn.residuals,
         dfbo_rn_RmPFC = fu_data.dfbo_rn_RmPFC_fu) %>% 
  mutate(dfbo_rn_RmPFC_col = case_when(dfbo_rn_RmPFC == 0 ~ "black",
                                      dfbo_rn_RmPFC == 1 ~ "red"))
plot_rn_RmPFC_lm <- rn_RmPFC_resid %>% 
  ggplot(aes(x = brn_resid, y = pfcs_resid)) +
  geom_point(color = factor(rn_RmPFC_resid$dfbo_rn_RmPFC_col)) +
  geom_smooth(method = "lm") + 
  xlab("Baseline RvN (z-score residuals)") + ylab("Follow-Up PFC-S Scores (z-score residuals)") + 
  theme_classic() +
  theme(legend.position = "none")
plot_rn_RmPFC_lm
```



