---
title: "S5. Concurrent Regression Analyses - Raw Condition Contrasts"
author: "Nicolas L. Camacho"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set working directory
knitr::opts_knit$set(root.dir = "C:/Users/nicol/Box/fMRI Reward/")
```

# Load packages
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(broom)
library(sensemakr)
library(lm.beta)
library(miceadds)
```

# Load dataset
```{r, message = FALSE}
base_data <- read_csv("final_share_dataset.csv") %>% 
  filter(base_sample == 1) %>% 
  dplyr::select(subj, z_child_age_base, z_bdi_mean_base, fam_code, z_pfc_s_mean_base,
                N_2018_LCaud, N_2018_RCaud, N_2021_RmPFC,
                R_2018_LCaud, R_2018_RCaud, R_2021_RmPFC,
                N_HO_LAmyg, L_HO_LAmyg, R_HO_LAmyg,
                N_HO_RAmyg, L_HO_RAmyg, R_HO_RAmyg) %>% 
  transmute(subj, z_child_age_base, z_bdi_mean_base, fam_code, z_pfc_s_mean_base,
            z_N_2018_LCaud = (N_2018_LCaud-mean(N_2018_LCaud))/sd(N_2018_LCaud),
            z_R_2018_LCaud = (R_2018_LCaud-mean(R_2018_LCaud))/sd(R_2018_LCaud),
            z_N_2018_RCaud = (N_2018_RCaud-mean(N_2018_RCaud))/sd(N_2018_RCaud),
            z_R_2018_RCaud = (R_2018_RCaud-mean(R_2018_RCaud))/sd(R_2018_RCaud),
            z_N_2021_RmPFC = (N_2021_RmPFC-mean(N_2021_RmPFC))/sd(N_2021_RmPFC),
            z_R_2021_RmPFC = (R_2021_RmPFC-mean(R_2021_RmPFC))/sd(R_2021_RmPFC),
            z_N_HO_LAmyg = (N_HO_LAmyg - mean(N_HO_LAmyg))/sd(N_HO_LAmyg),
            z_L_HO_LAmyg = (L_HO_LAmyg - mean(L_HO_LAmyg))/sd(L_HO_LAmyg),
            z_R_HO_LAmyg = (R_HO_LAmyg - mean(R_HO_LAmyg))/sd(R_HO_LAmyg),
            z_N_HO_RAmyg = (N_HO_RAmyg - mean(N_HO_RAmyg))/sd(N_HO_RAmyg),
            z_L_HO_RAmyg = (L_HO_RAmyg - mean(L_HO_RAmyg))/sd(L_HO_RAmyg),
            z_R_HO_RAmyg = (R_HO_RAmyg - mean(R_HO_RAmyg))/sd(R_HO_RAmyg))
```

# Run regression analyses (covariates: child age and parent BDI-II; clusters: according to family code; with and without outliers)

## Left Amygdala

### Reward
```{r}
# identify outliers
dfbo_r_lamyg_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_HO_LAmyg, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_lamyg_lm))) %>% 
  rename(., dfb_r_lamyg_base = z_R_HO_LAmyg) %>% 
  dplyr::select(., subj, dfb_r_lamyg_base) %>% 
  mutate(dfbo_r_lamyg_base = if_else(abs(dfb_r_lamyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_lamyg_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_r_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_r_lamyg_base == 0))
r_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_HO_LAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_r_lamyg_base == 0))
r_lamyg_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_HO_LAmyg, 
                               data = dplyr::filter(base_dfbo, dfbo_r_lamyg_base == 0))
summary(restrict_r_lamyg_noOut_lm)
summary(r_lamyg_noOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(r_lamyg_noOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.06744 - 0.04284 # R^2 change
glance(r_lamyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2
partial_f2(t_statistic = 2.6953746, dof = 105)

# run model with outliers
restrict_r_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
r_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_HO_LAmyg, 
                               cluster = "fam_code", data = base_data)
r_lamyg_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_HO_LAmyg, 
                               data = base_data)
summary(restrict_r_lamyg_withOut_lm)
summary(r_lamyg_withOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(r_lamyg_withOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.06424 - 0.0587 # R^2 change
glance(r_lamyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Loss
```{r}
# identify outliers
dfbo_l_lamyg_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_L_HO_LAmyg, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_l_lamyg_lm))) %>% 
  rename(., dfb_l_lamyg_base = z_L_HO_LAmyg) %>% 
  dplyr::select(., subj, dfb_l_lamyg_base) %>% 
  mutate(dfbo_l_lamyg_base = if_else(abs(dfb_l_lamyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_l_lamyg_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_l_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_l_lamyg_base == 0))
l_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_L_HO_LAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_l_lamyg_base == 0))
l_lamyg_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_L_HO_LAmyg, 
                               data = dplyr::filter(base_dfbo, dfbo_l_lamyg_base == 0))
summary(restrict_l_lamyg_noOut_lm)
summary(l_lamyg_noOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(l_lamyg_noOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.05918 - 0.05917 # R^2 change
glance(l_lamyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_l_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
l_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_L_HO_LAmyg, 
                               cluster = "fam_code", data = base_data)
l_lamyg_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_L_HO_LAmyg, 
                               data = base_data)
summary(restrict_l_lamyg_withOut_lm)
summary(l_lamyg_withOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(l_lamyg_withOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.06604 - 0.0587 # R^2 change
glance(l_lamyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_lamyg_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_N_HO_LAmyg, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_lamyg_lm))) %>% 
  rename(., dfb_n_lamyg_base = z_N_HO_LAmyg) %>% 
  dplyr::select(., subj, dfb_n_lamyg_base) %>% 
  mutate(dfbo_n_lamyg_base = if_else(abs(dfb_n_lamyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_lamyg_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_n_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_n_lamyg_base == 0))

n_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_HO_LAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_n_lamyg_base == 0))
n_lamyg_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_HO_LAmyg, 
                               data = dplyr::filter(base_dfbo, dfbo_n_lamyg_base == 0))
summary(restrict_n_lamyg_noOut_lm)
summary(n_lamyg_noOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(n_lamyg_noOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.09896 - 0.07444 # R^2 change
glance(n_lamyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2
partial_f2(t_statistic = 2.3690067, dof = 106)

# run model with outliers
restrict_n_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
n_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_HO_LAmyg, 
                               cluster = "fam_code", data = base_data)
n_lamyg_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_HO_LAmyg, 
                               data = base_data)
summary(restrict_n_lamyg_withOut_lm)
summary(n_lamyg_withOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(n_lamyg_withOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.06793 - 0.0587 # R^2 change
glance(n_lamyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### All conditions included at once
```{r}
# identify outliers
dfbo_rln_lamyg_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_HO_LAmyg + z_L_HO_LAmyg + z_N_HO_LAmyg, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rln_lamyg_lm))) %>% 
  rename(., dfb_r_lamyg_base = z_R_HO_LAmyg,
         dfb_l_lamyg_base = z_L_HO_LAmyg,
         dfb_n_lamyg_base = z_N_HO_LAmyg) %>% 
  dplyr::select(., subj, dfb_r_lamyg_base, dfb_l_lamyg_base, dfb_n_lamyg_base) %>% 
  mutate(dfbo_rln_lamyg_base = if_else(abs(dfb_r_lamyg_base) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_l_lamyg_base) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_lamyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_lamyg_base, dfb_l_lamyg_base, dfb_n_lamyg_base)) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_rln_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                            z_bdi_mean_base, cluster = "fam_code",
                                          data = dplyr::filter(base_dfbo, dfbo_rln_lamyg_base == 0))

rln_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_HO_LAmyg +
                                   z_L_HO_LAmyg + z_N_HO_LAmyg, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(base_dfbo, dfbo_rln_lamyg_base == 0))
rln_lamyg_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_HO_LAmyg + 
                                   z_L_HO_LAmyg + z_N_HO_LAmyg,
                                 data = dplyr::filter(base_dfbo, dfbo_rln_lamyg_base == 0))
summary(restrict_rln_lamyg_noOut_lm)
summary(rln_lamyg_noOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(rln_lamyg_noOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.11768 - 0.05862 # R^2 change
glance(rln_lamyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2
partial_f2(t_statistic = -1.82, dof = 98)
partial_f2(t_statistic = 2.19, dof = 98)

# run model with outliers
restrict_rln_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                              z_bdi_mean_base, cluster = "fam_code",
                                            data = base_data)
rln_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                     z_bdi_mean_base + z_R_HO_LAmyg +
                                     z_L_HO_LAmyg + z_N_HO_LAmyg,
                                   cluster = "fam_code", data = base_data)
rln_lamyg_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                     z_bdi_mean_base + z_R_HO_LAmyg +
                                     z_L_HO_LAmyg + z_N_HO_LAmyg,
                                   data = base_data)
summary(restrict_rln_lamyg_withOut_lm)
summary(rln_lamyg_withOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(rln_lamyg_withOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.09883 - 0.0587 # R^2 change
glance(rln_lamyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
partial_f2(t_statistic = -1.94, dof = 108)
```

## Right Amygdala

### Reward
```{r}
# identify outliers
dfbo_r_ramyg_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_HO_RAmyg, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_ramyg_lm))) %>% 
  rename(., dfb_r_ramyg_base = z_R_HO_RAmyg) %>% 
  dplyr::select(., subj, dfb_r_ramyg_base) %>% 
  mutate(dfbo_r_ramyg_base = if_else(abs(dfb_r_ramyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_ramyg_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_r_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_r_ramyg_base == 0))
r_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_HO_RAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_r_ramyg_base == 0))
r_ramyg_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_HO_RAmyg, 
                               data = dplyr::filter(base_dfbo, dfbo_r_ramyg_base == 0))
summary(restrict_r_ramyg_noOut_lm)
summary(r_ramyg_noOut_lm)
confint(r_ramyg_noOut_lm, level = 0.95)
0.08084 - 0.08075 # R^2 change
glance(r_ramyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_r_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
r_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_HO_RAmyg, 
                               cluster = "fam_code", data = base_data)
r_ramyg_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_HO_RAmyg, 
                               data = base_data)
summary(restrict_r_ramyg_withOut_lm)
summary(r_ramyg_withOut_lm)
confint(r_ramyg_withOut_lm, level = 0.95)
0.05884 - 0.0587 # R^2 change
glance(r_ramyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Loss
```{r}
# identify outliers
dfbo_l_ramyg_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_L_HO_RAmyg, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_l_ramyg_lm))) %>% 
  rename(., dfb_l_ramyg_base = z_L_HO_RAmyg) %>% 
  dplyr::select(., subj, dfb_l_ramyg_base) %>% 
  mutate(dfbo_l_ramyg_base = if_else(abs(dfb_l_ramyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_l_ramyg_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_l_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_l_ramyg_base == 0))
l_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_L_HO_RAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_l_ramyg_base == 0))
l_ramyg_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_L_HO_RAmyg, 
                               data = dplyr::filter(base_dfbo, dfbo_l_ramyg_base == 0))
summary(restrict_l_ramyg_noOut_lm)
summary(l_ramyg_noOut_lm)
confint(l_ramyg_noOut_lm, level = 0.95)
0.06391 - 0.06365 # R^2 change
glance(l_ramyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_l_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
l_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_L_HO_RAmyg, 
                               cluster = "fam_code", data = base_data)
l_ramyg_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_L_HO_RAmyg, 
                               data = base_data)
summary(restrict_l_ramyg_withOut_lm)
summary(l_ramyg_withOut_lm)
confint(l_ramyg_withOut_lm, level = 0.95)
0.05874 - 0.0587 # R^2 change
glance(l_ramyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_ramyg_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_N_HO_RAmyg, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_ramyg_lm))) %>% 
  rename(., dfb_n_ramyg_base = z_N_HO_RAmyg) %>% 
  dplyr::select(., subj, dfb_n_ramyg_base) %>% 
  mutate(dfbo_n_ramyg_base = if_else(abs(dfb_n_ramyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_ramyg_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_n_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_n_ramyg_base == 0))

n_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_HO_RAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_n_ramyg_base == 0))
n_ramyg_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_HO_RAmyg, 
                               data = dplyr::filter(base_dfbo, dfbo_n_ramyg_base == 0))
summary(restrict_n_ramyg_noOut_lm)
summary(n_ramyg_noOut_lm)
confint(n_ramyg_noOut_lm, level = 0.95)
0.03766 - 0.03222 # R^2 change
glance(n_ramyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_n_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
n_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_HO_RAmyg, 
                               cluster = "fam_code", data = base_data)
n_ramyg_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_HO_RAmyg, 
                               data = base_data)
summary(restrict_n_ramyg_withOut_lm)
summary(n_ramyg_withOut_lm)
confint(n_ramyg_withOut_lm, level = 0.95)
0.05879 - 0.0587 # R^2 change
glance(n_ramyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### All conditions included at once
```{r}
# identify outliers
dfbo_rln_ramyg_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_HO_RAmyg + z_L_HO_RAmyg + z_N_HO_RAmyg, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rln_ramyg_lm))) %>% 
  rename(., dfb_r_ramyg_base = z_R_HO_RAmyg,
         dfb_l_ramyg_base = z_L_HO_RAmyg,
         dfb_n_ramyg_base = z_N_HO_RAmyg) %>% 
  dplyr::select(., subj, dfb_r_ramyg_base, dfb_l_ramyg_base, dfb_n_ramyg_base) %>% 
  mutate(dfbo_rln_ramyg_base = if_else(abs(dfb_r_ramyg_base) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_l_ramyg_base) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_ramyg_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_ramyg_base, dfb_l_ramyg_base, dfb_n_ramyg_base)) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_rln_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                            z_bdi_mean_base, cluster = "fam_code",
                                          data = dplyr::filter(base_dfbo, dfbo_rln_ramyg_base == 0))

rln_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_HO_RAmyg +
                                   z_L_HO_RAmyg + z_N_HO_RAmyg, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(base_dfbo, dfbo_rln_ramyg_base == 0))
rln_ramyg_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_HO_RAmyg + 
                                   z_L_HO_RAmyg + z_N_HO_RAmyg,
                                 data = dplyr::filter(base_dfbo, dfbo_rln_ramyg_base == 0))
summary(restrict_rln_ramyg_noOut_lm)
summary(rln_ramyg_noOut_lm)
confint(rln_ramyg_noOut_lm, level = 0.95)
0.04476 - 0.04221 # R^2 change
glance(rln_ramyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_rln_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                              z_bdi_mean_base, cluster = "fam_code",
                                            data = base_data)
rln_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                     z_bdi_mean_base + z_R_HO_RAmyg +
                                     z_L_HO_RAmyg + z_N_HO_RAmyg,
                                   cluster = "fam_code", data = base_data)
rln_ramyg_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                     z_bdi_mean_base + z_R_HO_RAmyg +
                                     z_L_HO_RAmyg + z_N_HO_RAmyg,
                                   data = base_data)
summary(restrict_rln_ramyg_withOut_lm)
summary(rln_ramyg_withOut_lm)
confint(rln_ramyg_withOut_lm, level = 0.95)
0.05952 - 0.0587 # R^2 change
glance(rln_ramyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

## Left Caudate

### Reward
```{r}
# identify outliers
dfbo_r_lcaud_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_2018_LCaud, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_lcaud_lm))) %>% 
  rename(., dfb_r_lcaud_base = z_R_2018_LCaud) %>% 
  dplyr::select(., subj, dfb_r_lcaud_base) %>% 
  mutate(dfbo_r_lcaud_base = if_else(abs(dfb_r_lcaud_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_lcaud_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_r_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_r_lcaud_base == 0))
r_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2018_LCaud, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_r_lcaud_base == 0))
r_lcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2018_LCaud, 
                               data = dplyr::filter(base_dfbo, dfbo_r_lcaud_base == 0))
summary(restrict_r_lcaud_noOut_lm)
summary(r_lcaud_noOut_lm)
confint(r_lcaud_noOut_lm, level = 0.95)
0.08775 - 0.08387 # R^2 change
glance(r_lcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_r_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
r_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2018_LCaud, 
                               cluster = "fam_code", data = base_data)
r_lcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2018_LCaud, 
                               data = base_data)
summary(restrict_r_lcaud_withOut_lm)
summary(r_lcaud_withOut_lm)
confint(r_lcaud_withOut_lm, level = 0.95)
0.06067 - 0.0587 # R^2 change
glance(r_lcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_lcaud_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_N_2018_LCaud, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_lcaud_lm))) %>% 
  rename(., dfb_n_lcaud_base = z_N_2018_LCaud) %>% 
  dplyr::select(., subj, dfb_n_lcaud_base) %>% 
  mutate(dfbo_n_lcaud_base = if_else(abs(dfb_n_lcaud_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_lcaud_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_n_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_n_lcaud_base == 0))
n_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2018_LCaud, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_n_lcaud_base == 0))
n_lcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2018_LCaud, 
                               data = dplyr::filter(base_dfbo, dfbo_n_lcaud_base == 0))
summary(restrict_n_lcaud_noOut_lm)
summary(n_lcaud_noOut_lm)
confint(n_lcaud_noOut_lm, level = 0.95)
0.03607 - 0.03356 # R^2 change
glance(n_lcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_n_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
n_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2018_LCaud, 
                               cluster = "fam_code", data = base_data)
n_lcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2018_LCaud, 
                               data = base_data)
summary(restrict_n_lcaud_withOut_lm)
summary(n_lcaud_withOut_lm)
confint(n_lcaud_withOut_lm, level = 0.95)
0.06086 - 0.0587 # R^2 change
glance(n_lcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Reward and Neutral included at once
```{r}
# identify outliers
dfbo_rn_lcaud_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_2018_LCaud + z_N_2018_LCaud, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rn_lcaud_lm))) %>% 
  rename(., dfb_r_lcaud_base = z_R_2018_LCaud,
         dfb_n_lcaud_base = z_N_2018_LCaud) %>% 
  dplyr::select(., subj, dfb_r_lcaud_base, dfb_n_lcaud_base) %>% 
  mutate(dfbo_rn_lcaud_base = if_else(abs(dfb_r_lcaud_base) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_lcaud_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_lcaud_base, dfb_n_lcaud_base)) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_rn_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                            z_bdi_mean_base, cluster = "fam_code",
                                          data = dplyr::filter(base_dfbo, dfbo_rn_lcaud_base == 0))

rn_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_2018_LCaud + z_N_2018_LCaud, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(base_dfbo, dfbo_rn_lcaud_base == 0))
rn_lcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_2018_LCaud + z_N_2018_LCaud,
                                 data = dplyr::filter(base_dfbo, dfbo_rn_lcaud_base == 0))
summary(restrict_rn_lcaud_noOut_lm)
summary(rn_lcaud_noOut_lm)
confint(rn_lcaud_noOut_lm, level = 0.95)
0.0762 - 0.04236 # R^2 change
glance(rn_lcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2
partial_f2(t_statistic = -2.127393, dof = 96)

# run model with outliers
restrict_rn_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                              z_bdi_mean_base, cluster = "fam_code",
                                            data = base_data)
rn_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                     z_bdi_mean_base + z_R_2018_LCaud + z_N_2018_LCaud,
                                   cluster = "fam_code", data = base_data)
rn_lcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                     z_bdi_mean_base + z_R_2018_LCaud + z_N_2018_LCaud,
                                   data = base_data)
summary(restrict_rn_lcaud_withOut_lm)
summary(rn_lcaud_withOut_lm)
confint(rn_lcaud_withOut_lm, level = 0.95)
0.07164 - 0.0587 # R^2 change
glance(rn_lcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

## Right Caudate

### Reward
```{r}
# identify outliers
dfbo_r_rcaud_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_2018_RCaud, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_rcaud_lm))) %>% 
  rename(., dfb_r_rcaud_base = z_R_2018_RCaud) %>% 
  dplyr::select(., subj, dfb_r_rcaud_base) %>% 
  mutate(dfbo_r_rcaud_base = if_else(abs(dfb_r_rcaud_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_rcaud_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_r_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_r_rcaud_base == 0))
r_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2018_RCaud, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_r_rcaud_base == 0))
r_rcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2018_RCaud, 
                               data = dplyr::filter(base_dfbo, dfbo_r_rcaud_base == 0))
summary(restrict_r_rcaud_noOut_lm)
summary(r_rcaud_noOut_lm)
confint(r_rcaud_noOut_lm, level = 0.95)
0.1172 - 0.08776 # R^2 change
glance(r_rcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2
partial_f2(t_statistic = -2.13606344, dof = 100)

# run model with outliers
restrict_r_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
r_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2018_RCaud, 
                               cluster = "fam_code", data = base_data)
r_rcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2018_RCaud, 
                               data = base_data)
summary(restrict_r_rcaud_withOut_lm)
summary(r_rcaud_withOut_lm)
confint(r_rcaud_withOut_lm, level = 0.95)
0.06235 - 0.0587 # R^2 change
glance(r_rcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_rcaud_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_N_2018_RCaud, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_rcaud_lm))) %>% 
  rename(., dfb_n_rcaud_base = z_N_2018_RCaud) %>% 
  dplyr::select(., subj, dfb_n_rcaud_base) %>% 
  mutate(dfbo_n_rcaud_base = if_else(abs(dfb_n_rcaud_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_rcaud_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_n_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_n_rcaud_base == 0))
n_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2018_RCaud, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_n_rcaud_base == 0))
n_rcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2018_RCaud, 
                               data = dplyr::filter(base_dfbo, dfbo_n_rcaud_base == 0))
summary(restrict_n_rcaud_noOut_lm)
summary(n_rcaud_noOut_lm)
confint(n_rcaud_noOut_lm, level = 0.95)
0.06394 - 0.0631 # R^2 change
glance(n_rcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_n_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
n_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2018_RCaud, 
                               cluster = "fam_code", data = base_data)
n_rcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2018_RCaud, 
                               data = base_data)
summary(restrict_n_rcaud_withOut_lm)
summary(n_rcaud_withOut_lm)
confint(n_rcaud_withOut_lm, level = 0.95)
0.06198 - 0.0587 # R^2 change
glance(n_rcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Reward and Neutral included at once
```{r}
# identify outliers
dfbo_rn_rcaud_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_2018_RCaud + z_N_2018_RCaud, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rn_rcaud_lm))) %>% 
  rename(., dfb_r_rcaud_base = z_R_2018_RCaud,
         dfb_n_rcaud_base = z_N_2018_RCaud) %>% 
  dplyr::select(., subj, dfb_r_rcaud_base, dfb_n_rcaud_base) %>% 
  mutate(dfbo_rn_rcaud_base = if_else(abs(dfb_r_rcaud_base) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_rcaud_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_rcaud_base, dfb_n_rcaud_base)) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_rn_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                            z_bdi_mean_base, cluster = "fam_code",
                                          data = dplyr::filter(base_dfbo, dfbo_rn_rcaud_base == 0))

rn_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_2018_RCaud + z_N_2018_RCaud, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(base_dfbo, dfbo_rn_rcaud_base == 0))
rn_rcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_2018_RCaud + z_N_2018_RCaud,
                                 data = dplyr::filter(base_dfbo, dfbo_rn_rcaud_base == 0))
summary(restrict_rn_rcaud_noOut_lm)
summary(rn_rcaud_noOut_lm)
confint(rn_rcaud_noOut_lm, level = 0.95)
0.12059 - 0.05373 # R^2 change
glance(rn_rcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2
partial_f2(t_statistic = -3.20286639, dof = 94)
partial_f2(t_statistic = 2.604523599, dof = 94)

# run model with outliers
restrict_rn_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                              z_bdi_mean_base, cluster = "fam_code",
                                            data = base_data)
rn_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                     z_bdi_mean_base + z_R_2018_RCaud + z_N_2018_RCaud,
                                   cluster = "fam_code", data = base_data)
rn_rcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                     z_bdi_mean_base + z_R_2018_RCaud + z_N_2018_RCaud,
                                   data = base_data)
summary(restrict_rn_rcaud_withOut_lm)
summary(rn_rcaud_withOut_lm)
confint(rn_rcaud_withOut_lm, level = 0.95)
0.07777 - 0.0587 # R^2 change
glance(rn_rcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

## Right mPFC

### Reward
```{r}
# identify outliers
dfbo_r_rmpfc_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_2021_RmPFC, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_rmpfc_lm))) %>% 
  rename(., dfb_r_rmpfc_base = z_R_2021_RmPFC) %>% 
  dplyr::select(., subj, dfb_r_rmpfc_base) %>% 
  mutate(dfbo_r_rmpfc_base = if_else(abs(dfb_r_rmpfc_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_rmpfc_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_r_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_r_rmpfc_base == 0))
r_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2021_RmPFC, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_r_rmpfc_base == 0))
r_rmpfc_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2021_RmPFC, 
                               data = dplyr::filter(base_dfbo, dfbo_r_rmpfc_base == 0))
summary(restrict_r_rmpfc_noOut_lm)
summary(r_rmpfc_noOut_lm)
confint(r_rmpfc_noOut_lm, level = 0.95)
0.04791 - 0.04463 # R^2 change
glance(r_rmpfc_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_r_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
r_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2021_RmPFC, 
                               cluster = "fam_code", data = base_data)
r_rmpfc_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_R_2021_RmPFC, 
                               data = base_data)
summary(restrict_r_rmpfc_withOut_lm)
summary(r_rmpfc_withOut_lm)
confint(r_rmpfc_withOut_lm, level = 0.95)
0.05889 - 0.0587 # R^2 change
glance(r_rmpfc_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_rmpfc_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_N_2021_RmPFC, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_rmpfc_lm))) %>% 
  rename(., dfb_n_rmpfc_base = z_N_2021_RmPFC) %>% 
  dplyr::select(., subj, dfb_n_rmpfc_base) %>% 
  mutate(dfbo_n_rmpfc_base = if_else(abs(dfb_n_rmpfc_base) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_rmpfc_base) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_n_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = dplyr::filter(base_dfbo, dfbo_n_rmpfc_base == 0))
n_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2021_RmPFC, 
                               cluster = "fam_code",
                               data = dplyr::filter(base_dfbo, dfbo_n_rmpfc_base == 0))
n_rmpfc_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2021_RmPFC, 
                               data = dplyr::filter(base_dfbo, dfbo_n_rmpfc_base == 0))
summary(restrict_n_rmpfc_noOut_lm)
summary(n_rmpfc_noOut_lm)
confint(n_rmpfc_noOut_lm, level = 0.95)
0.06019 - 0.04651 # R^2 change
glance(n_rmpfc_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_n_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                          z_bdi_mean_base, cluster = "fam_code",
                                        data = base_data)
n_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2021_RmPFC, 
                               cluster = "fam_code", data = base_data)
n_rmpfc_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                 z_bdi_mean_base + z_N_2021_RmPFC, 
                               data = base_data)
summary(restrict_n_rmpfc_withOut_lm)
summary(n_rmpfc_withOut_lm)
confint(n_rmpfc_withOut_lm, level = 0.95)
0.0678 - 0.0587 # R^2 change
glance(n_rmpfc_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Reward and Neutral included at once
```{r}
# identify outliers
dfbo_rn_rmpfc_lm <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + z_bdi_mean_base +
                     z_R_2021_RmPFC + z_N_2021_RmPFC, data = base_data)
base_dfbo <- base_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rn_rmpfc_lm))) %>% 
  rename(., dfb_r_rmpfc_base = z_R_2021_RmPFC,
         dfb_n_rmpfc_base = z_N_2021_RmPFC) %>% 
  dplyr::select(., subj, dfb_r_rmpfc_base, dfb_n_rmpfc_base) %>% 
  mutate(dfbo_rn_rmpfc_base = if_else(abs(dfb_r_rmpfc_base) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_rmpfc_base) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_rmpfc_base, dfb_n_rmpfc_base)) %>% 
  left_join(base_data, ., by = "subj")

# run model wihout outliers
restrict_rn_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                            z_bdi_mean_base, cluster = "fam_code",
                                          data = dplyr::filter(base_dfbo, dfbo_rn_rmpfc_base == 0))

rn_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_2021_RmPFC + z_N_2021_RmPFC, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(base_dfbo, dfbo_rn_rmpfc_base == 0))
rn_rmpfc_noOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                   z_bdi_mean_base + z_R_2021_RmPFC + z_N_2021_RmPFC,
                                 data = dplyr::filter(base_dfbo, dfbo_rn_rmpfc_base == 0))
summary(restrict_rn_rmpfc_noOut_lm)
summary(rn_rmpfc_noOut_lm)
confint(rn_rmpfc_noOut_lm, level = 0.95)
0.10384 - 0.05222 # R^2 change
glance(rn_rmpfc_noOut_lm_noClust)$adj.r.squared # adjusted R^2
partial_f2(t_statistic = 2.7664034, dof = 99)

# run model with outliers
restrict_rn_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                              z_bdi_mean_base, cluster = "fam_code",
                                            data = base_data)
rn_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_base ~ 1 + z_child_age_base +
                                     z_bdi_mean_base + z_R_2021_RmPFC + z_N_2021_RmPFC,
                                   cluster = "fam_code", data = base_data)
rn_rmpfc_withOut_lm_noClust <- lm(z_pfc_s_mean_base ~ 1 + z_child_age_base + 
                                     z_bdi_mean_base + z_R_2021_RmPFC + z_N_2021_RmPFC,
                                   data = base_data)
summary(restrict_rn_rmpfc_withOut_lm)
summary(rn_rmpfc_withOut_lm)
confint(rn_rmpfc_withOut_lm, level = 0.95)
0.06988 - 0.0587 # R^2 change
glance(rn_rmpfc_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```


