---
title: "S6. Prospective Regression Analyses - Raw Condition Contrasts"
author: "Nicolas L. Camacho"
date: "2026-01-03"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set working directory
knitr::opts_knit$set(root.dir = "C:/Users/nicol/Box/fMRI Reward/")
```

# Load packages
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(broom)
library(sensemakr)
library(lm.beta)
library(miceadds)
```

# Load dataset
```{r, message = FALSE}
fu_data <- read_csv("final_share_dataset.csv") %>% 
  filter(fu_sample == 1) %>% 
  dplyr::select(subj, z_child_age_fu, z_bdi_mean_fu, fam_code, z_pfc_s_mean_fu,
                N_2018_LCaud, N_2018_RCaud, N_2021_RmPFC,
                R_2018_LCaud, R_2018_RCaud, R_2021_RmPFC,
                N_HO_LAmyg, L_HO_LAmyg, R_HO_LAmyg,
                N_HO_RAmyg, L_HO_RAmyg, R_HO_RAmyg) %>% 
  transmute(subj, z_child_age_fu, z_bdi_mean_fu, fam_code, z_pfc_s_mean_fu,
            z_N_2018_LCaud = (N_2018_LCaud-mean(N_2018_LCaud))/sd(N_2018_LCaud),
            z_R_2018_LCaud = (R_2018_LCaud-mean(R_2018_LCaud))/sd(R_2018_LCaud),
            z_N_2018_RCaud = (N_2018_RCaud-mean(N_2018_RCaud))/sd(N_2018_RCaud),
            z_R_2018_RCaud = (R_2018_RCaud-mean(R_2018_RCaud))/sd(R_2018_RCaud),
            z_N_2021_RmPFC = (N_2021_RmPFC-mean(N_2021_RmPFC))/sd(N_2021_RmPFC),
            z_R_2021_RmPFC = (R_2021_RmPFC-mean(R_2021_RmPFC))/sd(R_2021_RmPFC),
            z_N_HO_LAmyg = (N_HO_LAmyg - mean(N_HO_LAmyg))/sd(N_HO_LAmyg),
            z_L_HO_LAmyg = (L_HO_LAmyg - mean(L_HO_LAmyg))/sd(L_HO_LAmyg),
            z_R_HO_LAmyg = (R_HO_LAmyg - mean(R_HO_LAmyg))/sd(R_HO_LAmyg),
            z_N_HO_RAmyg = (N_HO_RAmyg - mean(N_HO_RAmyg))/sd(N_HO_RAmyg),
            z_L_HO_RAmyg = (L_HO_RAmyg - mean(L_HO_RAmyg))/sd(L_HO_RAmyg),
            z_R_HO_RAmyg = (R_HO_RAmyg - mean(R_HO_RAmyg))/sd(R_HO_RAmyg))
```

# Run regression analyses (covariates: child age and parent BDI-II; clusters: according to family code; with and without outliers)

## Left Amygdala

### Reward
```{r}
# identify outliers
dfbo_r_lamyg_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_HO_LAmyg, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_lamyg_lm))) %>% 
  rename(., dfb_r_lamyg_fu = z_R_HO_LAmyg) %>% 
  dplyr::select(., subj, dfb_r_lamyg_fu) %>% 
  mutate(dfbo_r_lamyg_fu = if_else(abs(dfb_r_lamyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_lamyg_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_r_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_r_lamyg_fu == 0))
r_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_HO_LAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_r_lamyg_fu == 0))
r_lamyg_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_HO_LAmyg, 
                               data = dplyr::filter(fu_dfbo, dfbo_r_lamyg_fu == 0))
summary(restrict_r_lamyg_noOut_lm)
summary(r_lamyg_noOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(r_lamyg_noOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.16761 - 0.16621 # R^2 change
glance(r_lamyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_r_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
r_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_HO_LAmyg, 
                               cluster = "fam_code", data = fu_data)
r_lamyg_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_HO_LAmyg, 
                               data = fu_data)
summary(restrict_r_lamyg_withOut_lm)
summary(r_lamyg_withOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(r_lamyg_withOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.12676 - 0.12671 # R^2 change
glance(r_lamyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Loss
```{r}
# identify outliers
dfbo_l_lamyg_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_L_HO_LAmyg, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_l_lamyg_lm))) %>% 
  rename(., dfb_l_lamyg_fu = z_L_HO_LAmyg) %>% 
  dplyr::select(., subj, dfb_l_lamyg_fu) %>% 
  mutate(dfbo_l_lamyg_fu = if_else(abs(dfb_l_lamyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_l_lamyg_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_l_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_l_lamyg_fu == 0))
l_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_L_HO_LAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_l_lamyg_fu == 0))
l_lamyg_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_L_HO_LAmyg, 
                               data = dplyr::filter(fu_dfbo, dfbo_l_lamyg_fu == 0))
summary(restrict_l_lamyg_noOut_lm)
summary(l_lamyg_noOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(l_lamyg_noOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.16675 - 0.15542 # R^2 change
glance(l_lamyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_l_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
l_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_L_HO_LAmyg, 
                               cluster = "fam_code", data = fu_data)
l_lamyg_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_L_HO_LAmyg, 
                               data = fu_data)
summary(restrict_l_lamyg_withOut_lm)
summary(l_lamyg_withOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(l_lamyg_withOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.13082 - 0.12671 # R^2 change
glance(l_lamyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_lamyg_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_N_HO_LAmyg, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_lamyg_lm))) %>% 
  rename(., dfb_n_lamyg_fu = z_N_HO_LAmyg) %>% 
  dplyr::select(., subj, dfb_n_lamyg_fu) %>% 
  mutate(dfbo_n_lamyg_fu = if_else(abs(dfb_n_lamyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_lamyg_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_n_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_n_lamyg_fu == 0))

n_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_HO_LAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_n_lamyg_fu == 0))
n_lamyg_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_HO_LAmyg, 
                               data = dplyr::filter(fu_dfbo, dfbo_n_lamyg_fu == 0))
summary(restrict_n_lamyg_noOut_lm)
summary(n_lamyg_noOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(n_lamyg_noOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.12584 - 0.12371 # R^2 change
glance(n_lamyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_n_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
n_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_HO_LAmyg, 
                               cluster = "fam_code", data = fu_data)
n_lamyg_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_HO_LAmyg, 
                               data = fu_data)
summary(restrict_n_lamyg_withOut_lm)
summary(n_lamyg_withOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(n_lamyg_withOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.1286 - 0.12671 # R^2 change
glance(n_lamyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### All conditions included at once
```{r}
# identify outliers
dfbo_rln_lamyg_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_HO_LAmyg + z_L_HO_LAmyg + z_N_HO_LAmyg, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rln_lamyg_lm))) %>% 
  rename(., dfb_r_lamyg_fu = z_R_HO_LAmyg,
         dfb_l_lamyg_fu = z_L_HO_LAmyg,
         dfb_n_lamyg_fu = z_N_HO_LAmyg) %>% 
  dplyr::select(., subj, dfb_r_lamyg_fu, dfb_l_lamyg_fu, dfb_n_lamyg_fu) %>% 
  mutate(dfbo_rln_lamyg_fu = if_else(abs(dfb_r_lamyg_fu) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_l_lamyg_fu) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_lamyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_lamyg_fu, dfb_l_lamyg_fu, dfb_n_lamyg_fu)) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_rln_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                            z_bdi_mean_fu, cluster = "fam_code",
                                          data = dplyr::filter(fu_dfbo, dfbo_rln_lamyg_fu == 0))

rln_lamyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_HO_LAmyg +
                                   z_L_HO_LAmyg + z_N_HO_LAmyg, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(fu_dfbo, dfbo_rln_lamyg_fu == 0))
rln_lamyg_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_HO_LAmyg + 
                                   z_L_HO_LAmyg + z_N_HO_LAmyg,
                                 data = dplyr::filter(fu_dfbo, dfbo_rln_lamyg_fu == 0))
summary(restrict_rln_lamyg_noOut_lm)
summary(rln_lamyg_noOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(rln_lamyg_noOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.2038 - 0.20004 # R^2 change
glance(rln_lamyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_rln_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                              z_bdi_mean_fu, cluster = "fam_code",
                                            data = fu_data)
rln_lamyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                     z_bdi_mean_fu + z_R_HO_LAmyg +
                                     z_L_HO_LAmyg + z_N_HO_LAmyg,
                                   cluster = "fam_code", data = fu_data)
rln_lamyg_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                     z_bdi_mean_fu + z_R_HO_LAmyg +
                                     z_L_HO_LAmyg + z_N_HO_LAmyg,
                                   data = fu_data)
summary(restrict_rln_lamyg_withOut_lm)
summary(rln_lamyg_withOut_lm) # divide fMRI predictor p-value by 2 given one-sided hypothesis
confint(rln_lamyg_withOut_lm, level = 0.90) # consider only upper limit for 95% CI
0.13278 - 0.12671 # R^2 change
glance(rln_lamyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

## Right Amygdala

### Reward
```{r}
# identify outliers
dfbo_r_ramyg_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_HO_RAmyg, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_ramyg_lm))) %>% 
  rename(., dfb_r_ramyg_fu = z_R_HO_RAmyg) %>% 
  dplyr::select(., subj, dfb_r_ramyg_fu) %>% 
  mutate(dfbo_r_ramyg_fu = if_else(abs(dfb_r_ramyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_ramyg_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_r_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_r_ramyg_fu == 0))
r_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_HO_RAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_r_ramyg_fu == 0))
r_ramyg_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_HO_RAmyg, 
                               data = dplyr::filter(fu_dfbo, dfbo_r_ramyg_fu == 0))
summary(restrict_r_ramyg_noOut_lm)
summary(r_ramyg_noOut_lm)
confint(r_ramyg_noOut_lm, level = 0.95)
0.19433 - 0.1885 # R^2 change
glance(r_ramyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_r_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
r_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_HO_RAmyg, 
                               cluster = "fam_code", data = fu_data)
r_ramyg_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_HO_RAmyg, 
                               data = fu_data)
summary(restrict_r_ramyg_withOut_lm)
summary(r_ramyg_withOut_lm)
confint(r_ramyg_withOut_lm, level = 0.95)
0.13364 - 0.12671 # R^2 change
glance(r_ramyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Loss
```{r}
# identify outliers
dfbo_l_ramyg_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_L_HO_RAmyg, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_l_ramyg_lm))) %>% 
  rename(., dfb_l_ramyg_fu = z_L_HO_RAmyg) %>% 
  dplyr::select(., subj, dfb_l_ramyg_fu) %>% 
  mutate(dfbo_l_ramyg_fu = if_else(abs(dfb_l_ramyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_l_ramyg_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_l_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_l_ramyg_fu == 0))
l_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_L_HO_RAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_l_ramyg_fu == 0))
l_ramyg_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_L_HO_RAmyg, 
                               data = dplyr::filter(fu_dfbo, dfbo_l_ramyg_fu == 0))
summary(restrict_l_ramyg_noOut_lm)
summary(l_ramyg_noOut_lm)
confint(l_ramyg_noOut_lm, level = 0.95)
0.13718 - 0.1328 # R^2 change
glance(l_ramyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_l_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
l_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_L_HO_RAmyg, 
                               cluster = "fam_code", data = fu_data)
l_ramyg_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_L_HO_RAmyg, 
                               data = fu_data)
summary(restrict_l_ramyg_withOut_lm)
summary(l_ramyg_withOut_lm)
confint(l_ramyg_withOut_lm, level = 0.95)
0.12753 - 0.12671 # R^2 change
glance(l_ramyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_ramyg_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_N_HO_RAmyg, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_ramyg_lm))) %>% 
  rename(., dfb_n_ramyg_fu = z_N_HO_RAmyg) %>% 
  dplyr::select(., subj, dfb_n_ramyg_fu) %>% 
  mutate(dfbo_n_ramyg_fu = if_else(abs(dfb_n_ramyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_ramyg_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_n_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_n_ramyg_fu == 0))

n_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_HO_RAmyg, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_n_ramyg_fu == 0))
n_ramyg_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_HO_RAmyg, 
                               data = dplyr::filter(fu_dfbo, dfbo_n_ramyg_fu == 0))
summary(restrict_n_ramyg_noOut_lm)
summary(n_ramyg_noOut_lm)
confint(n_ramyg_noOut_lm, level = 0.95)
0.1782 - 0.1703 # R^2 change
glance(n_ramyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_n_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
n_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_HO_RAmyg, 
                               cluster = "fam_code", data = fu_data)
n_ramyg_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_HO_RAmyg, 
                               data = fu_data)
summary(restrict_n_ramyg_withOut_lm)
summary(n_ramyg_withOut_lm)
confint(n_ramyg_withOut_lm, level = 0.95)
0.13975 - 0.12671 # R^2 change
glance(n_ramyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### All conditions included at once
```{r}
# identify outliers
dfbo_rln_ramyg_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_HO_RAmyg + z_L_HO_RAmyg + z_N_HO_RAmyg, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rln_ramyg_lm))) %>% 
  rename(., dfb_r_ramyg_fu = z_R_HO_RAmyg,
         dfb_l_ramyg_fu = z_L_HO_RAmyg,
         dfb_n_ramyg_fu = z_N_HO_RAmyg) %>% 
  dplyr::select(., subj, dfb_r_ramyg_fu, dfb_l_ramyg_fu, dfb_n_ramyg_fu) %>% 
  mutate(dfbo_rln_ramyg_fu = if_else(abs(dfb_r_ramyg_fu) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_l_ramyg_fu) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_ramyg_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_ramyg_fu, dfb_l_ramyg_fu, dfb_n_ramyg_fu)) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_rln_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                            z_bdi_mean_fu, cluster = "fam_code",
                                          data = dplyr::filter(fu_dfbo, dfbo_rln_ramyg_fu == 0))

rln_ramyg_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_HO_RAmyg +
                                   z_L_HO_RAmyg + z_N_HO_RAmyg, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(fu_dfbo, dfbo_rln_ramyg_fu == 0))
rln_ramyg_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_HO_RAmyg + 
                                   z_L_HO_RAmyg + z_N_HO_RAmyg,
                                 data = dplyr::filter(fu_dfbo, dfbo_rln_ramyg_fu == 0))
summary(restrict_rln_ramyg_noOut_lm)
summary(rln_ramyg_noOut_lm)
confint(rln_ramyg_noOut_lm, level = 0.95)
0.21668 - 0.17766 # R^2 change
glance(rln_ramyg_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_rln_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                              z_bdi_mean_fu, cluster = "fam_code",
                                            data = fu_data)
rln_ramyg_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                     z_bdi_mean_fu + z_R_HO_RAmyg +
                                     z_L_HO_RAmyg + z_N_HO_RAmyg,
                                   cluster = "fam_code", data = fu_data)
rln_ramyg_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                     z_bdi_mean_fu + z_R_HO_RAmyg +
                                     z_L_HO_RAmyg + z_N_HO_RAmyg,
                                   data = fu_data)
summary(restrict_rln_ramyg_withOut_lm)
summary(rln_ramyg_withOut_lm)
confint(rln_ramyg_withOut_lm, level = 0.95)
0.14794 - 0.12671 # R^2 change
glance(rln_ramyg_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

## Left Caudate

### Reward
```{r}
# identify outliers
dfbo_r_lcaud_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_2018_LCaud, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_lcaud_lm))) %>% 
  rename(., dfb_r_lcaud_fu = z_R_2018_LCaud) %>% 
  dplyr::select(., subj, dfb_r_lcaud_fu) %>% 
  mutate(dfbo_r_lcaud_fu = if_else(abs(dfb_r_lcaud_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_lcaud_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_r_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_r_lcaud_fu == 0))
r_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2018_LCaud, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_r_lcaud_fu == 0))
r_lcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2018_LCaud, 
                               data = dplyr::filter(fu_dfbo, dfbo_r_lcaud_fu == 0))
summary(restrict_r_lcaud_noOut_lm)
summary(r_lcaud_noOut_lm)
confint(r_lcaud_noOut_lm, level = 0.95)
0.19285 - 0.18513 # R^2 change
glance(r_lcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_r_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
r_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2018_LCaud, 
                               cluster = "fam_code", data = fu_data)
r_lcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2018_LCaud, 
                               data = fu_data)
summary(restrict_r_lcaud_withOut_lm)
summary(r_lcaud_withOut_lm)
confint(r_lcaud_withOut_lm, level = 0.95)
0.12855 - 0.12671 # R^2 change
glance(r_lcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_lcaud_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_N_2018_LCaud, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_lcaud_lm))) %>% 
  rename(., dfb_n_lcaud_fu = z_N_2018_LCaud) %>% 
  dplyr::select(., subj, dfb_n_lcaud_fu) %>% 
  mutate(dfbo_n_lcaud_fu = if_else(abs(dfb_n_lcaud_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_lcaud_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_n_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_n_lcaud_fu == 0))
n_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2018_LCaud, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_n_lcaud_fu == 0))
n_lcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2018_LCaud, 
                               data = dplyr::filter(fu_dfbo, dfbo_n_lcaud_fu == 0))
summary(restrict_n_lcaud_noOut_lm)
summary(n_lcaud_noOut_lm)
confint(n_lcaud_noOut_lm, level = 0.95)
0.14638 - 0.13935 # R^2 change
glance(n_lcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_n_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
n_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2018_LCaud, 
                               cluster = "fam_code", data = fu_data)
n_lcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2018_LCaud, 
                               data = fu_data)
summary(restrict_n_lcaud_withOut_lm)
summary(n_lcaud_withOut_lm)
confint(n_lcaud_withOut_lm, level = 0.95)
0.12724 - 0.12671 # R^2 change
glance(n_lcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Reward and Neutral included at once
```{r}
# identify outliers
dfbo_rn_lcaud_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_2018_LCaud + z_N_2018_LCaud, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rn_lcaud_lm))) %>% 
  rename(., dfb_r_lcaud_fu = z_R_2018_LCaud,
         dfb_n_lcaud_fu = z_N_2018_LCaud) %>% 
  dplyr::select(., subj, dfb_r_lcaud_fu, dfb_n_lcaud_fu) %>% 
  mutate(dfbo_rn_lcaud_fu = if_else(abs(dfb_r_lcaud_fu) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_lcaud_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_lcaud_fu, dfb_n_lcaud_fu)) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_rn_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                            z_bdi_mean_fu, cluster = "fam_code",
                                          data = dplyr::filter(fu_dfbo, dfbo_rn_lcaud_fu == 0))

rn_lcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_2018_LCaud + z_N_2018_LCaud, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(fu_dfbo, dfbo_rn_lcaud_fu == 0))
rn_lcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_2018_LCaud + z_N_2018_LCaud,
                                 data = dplyr::filter(fu_dfbo, dfbo_rn_lcaud_fu == 0))
summary(restrict_rn_lcaud_noOut_lm)
summary(rn_lcaud_noOut_lm)
confint(rn_lcaud_noOut_lm, level = 0.95)
0.20599 - 0.1822 # R^2 change
glance(rn_lcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_rn_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                              z_bdi_mean_fu, cluster = "fam_code",
                                            data = fu_data)
rn_lcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                     z_bdi_mean_fu + z_R_2018_LCaud + z_N_2018_LCaud,
                                   cluster = "fam_code", data = fu_data)
rn_lcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                     z_bdi_mean_fu + z_R_2018_LCaud + z_N_2018_LCaud,
                                   data = fu_data)
summary(restrict_rn_lcaud_withOut_lm)
summary(rn_lcaud_withOut_lm)
confint(rn_lcaud_withOut_lm, level = 0.95)
0.13322 - 0.12671 # R^2 change
glance(rn_lcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

## Right Caudate

### Reward
```{r}
# identify outliers
dfbo_r_rcaud_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_2018_RCaud, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_rcaud_lm))) %>% 
  rename(., dfb_r_rcaud_fu = z_R_2018_RCaud) %>% 
  dplyr::select(., subj, dfb_r_rcaud_fu) %>% 
  mutate(dfbo_r_rcaud_fu = if_else(abs(dfb_r_rcaud_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_rcaud_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_r_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_r_rcaud_fu == 0))
r_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2018_RCaud, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_r_rcaud_fu == 0))
r_rcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2018_RCaud, 
                               data = dplyr::filter(fu_dfbo, dfbo_r_rcaud_fu == 0))
summary(restrict_r_rcaud_noOut_lm)
summary(r_rcaud_noOut_lm)
confint(r_rcaud_noOut_lm, level = 0.95)
0.2005 - 0.19707 # R^2 change
glance(r_rcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_r_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
r_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2018_RCaud, 
                               cluster = "fam_code", data = fu_data)
r_rcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2018_RCaud, 
                               data = fu_data)
summary(restrict_r_rcaud_withOut_lm)
summary(r_rcaud_withOut_lm)
confint(r_rcaud_withOut_lm, level = 0.95)
0.12725 - 0.12671 # R^2 change
glance(r_rcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_rcaud_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_N_2018_RCaud, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_rcaud_lm))) %>% 
  rename(., dfb_n_rcaud_fu = z_N_2018_RCaud) %>% 
  dplyr::select(., subj, dfb_n_rcaud_fu) %>% 
  mutate(dfbo_n_rcaud_fu = if_else(abs(dfb_n_rcaud_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_rcaud_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_n_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_n_rcaud_fu == 0))
n_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2018_RCaud, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_n_rcaud_fu == 0))
n_rcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2018_RCaud, 
                               data = dplyr::filter(fu_dfbo, dfbo_n_rcaud_fu == 0))
summary(restrict_n_rcaud_noOut_lm)
summary(n_rcaud_noOut_lm)
confint(n_rcaud_noOut_lm, level = 0.95)
0.14323 - 0.14321 # R^2 change
glance(n_rcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_n_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
n_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2018_RCaud, 
                               cluster = "fam_code", data = fu_data)
n_rcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2018_RCaud, 
                               data = fu_data)
summary(restrict_n_rcaud_withOut_lm)
summary(n_rcaud_withOut_lm)
confint(n_rcaud_withOut_lm, level = 0.95)
0.1268 - 0.12671 # R^2 change
glance(n_rcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Reward and Neutral included at once
```{r}
# identify outliers
dfbo_rn_rcaud_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_2018_RCaud + z_N_2018_RCaud, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rn_rcaud_lm))) %>% 
  rename(., dfb_r_rcaud_fu = z_R_2018_RCaud,
         dfb_n_rcaud_fu = z_N_2018_RCaud) %>% 
  dplyr::select(., subj, dfb_r_rcaud_fu, dfb_n_rcaud_fu) %>% 
  mutate(dfbo_rn_rcaud_fu = if_else(abs(dfb_r_rcaud_fu) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_rcaud_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_rcaud_fu, dfb_n_rcaud_fu)) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_rn_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                            z_bdi_mean_fu, cluster = "fam_code",
                                          data = dplyr::filter(fu_dfbo, dfbo_rn_rcaud_fu == 0))

rn_rcaud_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_2018_RCaud + z_N_2018_RCaud, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(fu_dfbo, dfbo_rn_rcaud_fu == 0))
rn_rcaud_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_2018_RCaud + z_N_2018_RCaud,
                                 data = dplyr::filter(fu_dfbo, dfbo_rn_rcaud_fu == 0))
summary(restrict_rn_rcaud_noOut_lm)
summary(rn_rcaud_noOut_lm)
confint(rn_rcaud_noOut_lm, level = 0.95)
0.26278 - 0.21038 # R^2 change
glance(rn_rcaud_noOut_lm_noClust)$adj.r.squared # adjusted R^2
partial_f2(t_statistic = -2.4232278, dof = 60)

# run model with outliers
restrict_rn_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                              z_bdi_mean_fu, cluster = "fam_code",
                                            data = fu_data)
rn_rcaud_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                     z_bdi_mean_fu + z_R_2018_RCaud + z_N_2018_RCaud,
                                   cluster = "fam_code", data = fu_data)
rn_rcaud_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                     z_bdi_mean_fu + z_R_2018_RCaud + z_N_2018_RCaud,
                                   data = fu_data)
summary(restrict_rn_rcaud_withOut_lm)
summary(rn_rcaud_withOut_lm)
confint(rn_rcaud_withOut_lm, level = 0.95)
0.12821 - 0.12671 # R^2 change
glance(rn_rcaud_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

## Right mPFC

### Reward
```{r}
# identify outliers
dfbo_r_rmpfc_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_2021_RmPFC, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_r_rmpfc_lm))) %>% 
  rename(., dfb_r_rmpfc_fu = z_R_2021_RmPFC) %>% 
  dplyr::select(., subj, dfb_r_rmpfc_fu) %>% 
  mutate(dfbo_r_rmpfc_fu = if_else(abs(dfb_r_rmpfc_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_r_rmpfc_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_r_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_r_rmpfc_fu == 0))
r_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2021_RmPFC, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_r_rmpfc_fu == 0))
r_rmpfc_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2021_RmPFC, 
                               data = dplyr::filter(fu_dfbo, dfbo_r_rmpfc_fu == 0))
summary(restrict_r_rmpfc_noOut_lm)
summary(r_rmpfc_noOut_lm)
confint(r_rmpfc_noOut_lm, level = 0.95)
0.14926 - 0.14431 # R^2 change
glance(r_rmpfc_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_r_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
r_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2021_RmPFC, 
                               cluster = "fam_code", data = fu_data)
r_rmpfc_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_R_2021_RmPFC, 
                               data = fu_data)
summary(restrict_r_rmpfc_withOut_lm)
summary(r_rmpfc_withOut_lm)
confint(r_rmpfc_withOut_lm, level = 0.95)
0.14077 - 0.12671 # R^2 change
glance(r_rmpfc_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Neutral
```{r}
# identify outliers
dfbo_n_rmpfc_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_N_2021_RmPFC, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_n_rmpfc_lm))) %>% 
  rename(., dfb_n_rmpfc_fu = z_N_2021_RmPFC) %>% 
  dplyr::select(., subj, dfb_n_rmpfc_fu) %>% 
  mutate(dfbo_n_rmpfc_fu = if_else(abs(dfb_n_rmpfc_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>% 
  dplyr::select(., -dfb_n_rmpfc_fu) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_n_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = dplyr::filter(fu_dfbo, dfbo_n_rmpfc_fu == 0))
n_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2021_RmPFC, 
                               cluster = "fam_code",
                               data = dplyr::filter(fu_dfbo, dfbo_n_rmpfc_fu == 0))
n_rmpfc_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2021_RmPFC, 
                               data = dplyr::filter(fu_dfbo, dfbo_n_rmpfc_fu == 0))
summary(restrict_n_rmpfc_noOut_lm)
summary(n_rmpfc_noOut_lm)
confint(n_rmpfc_noOut_lm, level = 0.95)
0.14034 - 0.13735 # R^2 change
glance(n_rmpfc_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_n_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                          z_bdi_mean_fu, cluster = "fam_code",
                                        data = fu_data)
n_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2021_RmPFC, 
                               cluster = "fam_code", data = fu_data)
n_rmpfc_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                 z_bdi_mean_fu + z_N_2021_RmPFC, 
                               data = fu_data)
summary(restrict_n_rmpfc_withOut_lm)
summary(n_rmpfc_withOut_lm)
confint(n_rmpfc_withOut_lm, level = 0.95)
0.12674 - 0.12671 # R^2 change
glance(n_rmpfc_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```

### Reward and Neutral included at once
```{r}
# identify outliers
dfbo_rn_rmpfc_lm <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + z_bdi_mean_fu +
                     z_R_2021_RmPFC + z_N_2021_RmPFC, data = fu_data)
fu_dfbo <- fu_data %>% dplyr::select(., subj) %>% 
  bind_cols(., data.frame(dfbetas(dfbo_rn_rmpfc_lm))) %>% 
  rename(., dfb_r_rmpfc_fu = z_R_2021_RmPFC,
         dfb_n_rmpfc_fu = z_N_2021_RmPFC) %>% 
  dplyr::select(., subj, dfb_r_rmpfc_fu, dfb_n_rmpfc_fu) %>% 
  mutate(dfbo_rn_rmpfc_fu = if_else(abs(dfb_r_rmpfc_fu) < 2/sqrt(length(.$subj)) &
                                         abs(dfb_n_rmpfc_fu) < 2/sqrt(length(.$subj)), 0, 1)) %>%
  dplyr::select(., -c(dfb_r_rmpfc_fu, dfb_n_rmpfc_fu)) %>% 
  left_join(fu_data, ., by = "subj")

# run model wihout outliers
restrict_rn_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                            z_bdi_mean_fu, cluster = "fam_code",
                                          data = dplyr::filter(fu_dfbo, dfbo_rn_rmpfc_fu == 0))

rn_rmpfc_noOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_2021_RmPFC + z_N_2021_RmPFC, 
                                 cluster = "fam_code",
                                 data = dplyr::filter(fu_dfbo, dfbo_rn_rmpfc_fu == 0))
rn_rmpfc_noOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                   z_bdi_mean_fu + z_R_2021_RmPFC + z_N_2021_RmPFC,
                                 data = dplyr::filter(fu_dfbo, dfbo_rn_rmpfc_fu == 0))
summary(restrict_rn_rmpfc_noOut_lm)
summary(rn_rmpfc_noOut_lm)
confint(rn_rmpfc_noOut_lm, level = 0.95)
0.2017 - 0.18718 # R^2 change
glance(rn_rmpfc_noOut_lm_noClust)$adj.r.squared # adjusted R^2

# run model with outliers
restrict_rn_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                              z_bdi_mean_fu, cluster = "fam_code",
                                            data = fu_data)
rn_rmpfc_withOut_lm <- lm.cluster(z_pfc_s_mean_fu ~ 1 + z_child_age_fu +
                                     z_bdi_mean_fu + z_R_2021_RmPFC + z_N_2021_RmPFC,
                                   cluster = "fam_code", data = fu_data)
rn_rmpfc_withOut_lm_noClust <- lm(z_pfc_s_mean_fu ~ 1 + z_child_age_fu + 
                                     z_bdi_mean_fu + z_R_2021_RmPFC + z_N_2021_RmPFC,
                                   data = fu_data)
summary(restrict_rn_rmpfc_withOut_lm)
summary(rn_rmpfc_withOut_lm)
confint(rn_rmpfc_withOut_lm, level = 0.95)
0.14393 - 0.12671 # R^2 change
glance(rn_rmpfc_withOut_lm_noClust)$adj.r.squared # adjusted R^2
```



